\beginsong{4 Chord Song}[
    wuw={Axis of Awesome}, 
    jahr={2009}, 
    alb={Animal Vehicle}, 
    index={Four Chord Song},
]

\renewcommand{\everychorus}{\textnote{\bf}}
\beginchorus
\[C]My life is brilliant,\[G] my love is pure,\[Am] I saw an angel\[F] of that I'm sure.
\[C]People killing people \[G]dying, Children hurt you hear them \[Am]crying 
Can you practice what you \[F]preach? Would you turn the other \[C]cheek?
Forever \[G]young, I want to \[Am]be forever \[F]young.
\[C]I won't hesi\[G]tate no more, no \[Am]more, It cannot \[F]wait, I'm yours.
Your \[C]lipstick stains\[G] on the front lobe of my \[Am]left side brains, 
\[F] I knew I wouldn't for\[C]get you. 
If I could\[G]{, then} I would\[Am], I'll go wher\[F]ever you will go
And \[C]can you \[G]feel the \[Am]love to\[F]night?
\[C] Nobody want's to \[G]see us together, \[Am]but it don't matter \[F]no \echo{'Cause I got you.}
Country \[C]roads, take me \[G]home, to the \[Am]place I be\[F]long.
\[C]I'm your biggest fan, I'll \[G]follow you until you \[Am]love me. Papa-\[F]Paparazzi.
I can't \[C]live\[G]{, with} or with\[Am]out you! \[F]
Pictures of \[C]you, pictures of \[G]me, hung upon your \[Am]wall for the world to \[F]see.
And she \[C]will be \[G]loved, she \[Am]will be \[F]loved
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Double Time}}
\beginchorus
When I \[C]find myself in \[G]times of trouble, \[Am]Mother Mary co\[F]mes to me.
\[C]No, \[G]woman, no \[Am]cry. Yeah, Mama this s\[F]urely is a dr\[C]eam.
I come from a \[G]land down under... \[Am] \[F]
\[C]Red, white and \[G]blue all the \[Am]funny things you \[F]do.
Ameri\[C]ca, Ameri\[G]ca, This is \[Am]you. \[F]\newpage
They say that \[C]Taylor was a good girl \[G]never one to be late,
\[Am]complain express \[F]ideas in her brain.
I \[C]need some love, like I've \[G]never needed love be\[Am]fore,
I'm gonna make love \[F]to ya baby.
\[C]Take \[G]on \[Am]me, \echo{\[F]When I come around}
\[C]Take \[G]me \[Am]on, \echo{\[F]When I come around}
\[C]I'll \[G]be \[Am]gone, \[F]When I'm on \[C]take. \[G] \[Am] \[F]

\[C] \[G]Save to\[Am]night. \echo{It's gonna take a lot\[F] to drag me away from you}
and \[C]fight the break of \[G]dawn co\[Am]me tomorrow \[F] 
\echo{Theres nothing that a hundred men or more could ever do}
To\[C]morrow I'll be \[G]gone. \echo{If I were a boy,}
Here I \[Am]am, once a\[F]gain, \echo{I think I could understand}
I'm \[C]torn into \[G]pieces
Can't de\[Am]ny it, can't pre\[F]tend, just tho\[C]ught you were the o\[G]ne
In my \[Am]head, I \[F]see \[C]you all over \[G]me.
In my \[Am]head, \[F]you ful\[C]fill my fanta\[G]sy. In my head.

De\[Am]spite all my \[F]rage I am \[C]still just a \[G]rat in a cage.
\echo{What if \[Am]God was \[F]one of us? \[C] \[G] }
Tell me: \[Am]Why'd you have to go and make \[F]things so compli\[C]cated?
I \[G]see the way you're... \echo{\[Am]Actin like you're somebody...}
I \[F]know she's \[C]playin with \[G]me,\[Am] but that's \[F]ok, coz I got \[C]no self es\[G]teem.
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Back to normal speed}}
\beginchorus
With a \[Am]thousand eyes and a \[F]great disguise, 
hit em \[C]right between the eyes, hit them \[G]right between the eyes.\newpage
You're so \[Am]beautiful\[F], so damn \[C]beautif\[G]ul.
It's \[Am]too late to apolo\[F]gize, \[C]too late. \[G]
Just gonna st\[Am]and there and watch me \[F]burn,
but that's al\[C]right because I like the way it \[G]hurts.

It's my \[Am]life, it's \[F]now or never\[C]{, I} ain't gonna \[G]live forever!
\[Am]Can't read my, can't read \[F]my, no he can't read my \[C]poker face...
\echo{\[G]Come on Barbie, let's go party!}
\[Am]How long how \[F]long will I \[C]slide, \[G]separate my... 
\[Am]Double rainbow all the way a\[F]cross the sky. \[C]Yeah, yeah,\[G] so intense.
\[Am] Control yourself\[F]{, }take only what you \[C]need from him. \[G]
\[Am] A family of \[F]trees wanting.
\[C]Time to\[G] say good\[Am]bye, \echo{Vede\[F]tto, vissuto con te.}
% Should \[C]auld acquaintance \[G]be forgot, and \[Am]never brought to m\[F]ind?
Nehmt \[C]Abschied Brüder, \[G]ungewiss ist \[Am]alle Wieder\[F]kehr.
I'm more than a \[C]bird, I'm more than a \[G]plane,
I'm a \[Am]birdplane\[F], I'm a bi\[C]rdplane\[G], a mother fuckin' bi\[Am]rdplane. \[F]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Finé}}
\beginchorus
And doesn't that sound fa\[C]miliar? Doesn't that hit too \[G]close to home?
Doesn't that make you \[Am]shiver? The way that things have go\[F]ne.
And doesn't that seem pe\[C]culiar, 'cause everyone wants a \[G]little more?
It's something I do re\[Am]member to never go this \[F]far,
that's all it takes to be a \[C]STAR! \[C]
\endchorus

\endsong
