\beginsong{All Star }[wuw={Smash Mouth}, jahr=1999, alb={Astro Lounge}, index={Somebody once told me}]

\interlude{Intro: \[D A Em G ~~~ D A Em G]}

\beginverse\memorize
Some\[D]body once \[A]told me the \[Em]world is gonna \[G]roll me,
I \[D]ain’t the sharpest \[A]tool in the \[Em]shed. \[G]
She was \[D]looking kind of \[A]dumb with her \[Em]finger and her \[G]thumb,
with the \[D]shape of an \[A]''L'' on her \[Em]forehead \[G].
~
Well the \[D]years start coming and they \[A]don’t stop coming,
\[Em]back to the rule and I \[G]hit the ground running.
\[D]Didn’t make sense not to \[A]live for fun,
your \[Em]brain gets smart and your \[G]head gets dumb.
\[D]So much to do, so \[A]much to see, so what’s 
\[Em]wrong with taking the \[G]back streets?
You’ll \[D]never know if you don’t \[A]go, you’ll \[Em]never shine if you don’t \[G]glow!
\endverse

\beginchorus
\[D]Hey now you’re an \[A]All Star, get your \[Em]game on, \[G]go play!
\[D]Hey now you’re a \[A]Rock Star, get the \[Em]show on \[G]get paid!
And \[D]all the \[A]glitters are \[Hm]gold, \[G]only shooting \[D]stars \[C]break the \[G]mold.
\endchorus

\beginverse
It’s a ^cool place and they ^say it gets colder,
you’re ^bundled up now, wait ^’till you get older.
but the ^meteor men beg a ^differ judging by the 
^hole in the satellite ^picture.
\newpage
The ice we ^skate is getting pretty ^thin 
the water’s getting ^warm so you might as well ^swim
My world’s on ^fire how about ^yours that’s the way I 
^like it and I never get ^bored
\endverse

\printchorus
% \interlude{Zwischenspiel: \[D A Em G]}
% \printchorus

\beginverse
Some^body once ^asked ''Could I ^spare some change for ^gas,
I need to ^get myself aw^ay from this ^place.'' ^
I said ^''Yep, what a con^cept, I could ^use a little fuel my^self
and we could ^all use a ^little ^change.'' ^
~
Well the ^years start coming and they ^don’t stop coming,
 ^back to the rule and I ^hit the ground running.
^Didn’t make sense not to ^live for fun,
your ^brain gets smart and your ^head gets dumb.
^So much to do, so ^much to see, so what’s 
^wrong with taking the ^back streets?
You’ll ^never know if you don’t ^go, you’ll ^never shine if you don’t ^glow!
\endverse


% \beginchorus
% \[D]Hey now you’re an \[A]All Star, get your \[Em]game on,\[G]go play!
% \[D]Hey now you’re a \[A]Rock Star, get the \[Em]show on \[G]get paid!
% And \[D]all the \[A]glitters are \[Hm]gold, only shooting \[D]stars \[C]break the \[G]mold.
% \endchorus
\printchorus

\endsong
