\beginsong{Along Comes Mary}[
    wuw={Bloodhound Gang}, 
    alb={Hooray for Boobies}, 
    jahr={2000},
]

\beginverse
\[G]Every time I think that I'm the \[D]only one 
who's lonely someone \[D#]calls on \[Cm]me.
And \[G]every now and then I spend my \[D]time in rhyme 
and verse and curse those \[D#]faults in \[Cm]me.
And then a\[G]long comes Mary, \echo{\[B&]Mary, Mary} 
then a\[G]long comes Mary, \echo{\[B&]Mary, Mary}
and does she \[G]want to give me \[D]kicks, 
and be my \[D#]steady chick and \[Cm]give me pick of \[G]memories, \[B&]
or maybe \[G]rather gather \[D]tales 
of all the \[D#]fails and tribu\[Cm]lations no one \[G]ever sees. \[B&]
\endverse

\beginchorus
\[D]When we \[D#]met I was sure out \[D]to \[Cm]lunch,
now my \[D]empty \[G]cup tastes as sweet as \[F]the \[B&]punch, sweet as the punch.
{\nolyrics \[G G G] \[Cm] \[D D D] \[Cm] \[D# D# D#] \[D] \[C C C] \[D] \rep{2}}
\endchorus

\beginverse
When vague de^sire is the fire in the ^eyes of chicks,
whose sickness is the ^games they ^play.
And when the ^masquerade is played and neighbour ^folks make jokes
as who is most to ^blame to^day
And then a^long comes Mary, \echo{^Mary, Mary} 
then a^long comes Mary, \echo{^Mary, Mary}\newpage
And does she ^want to set them ^free, 
and let them ^see reali^ty from where she ^got her name, ^
and will they ^struggle much when ^told 
that such a ^tender touch as ^hers will make them ^not the same. ^
\endverse

\printchorus

\beginverse
And when the ^morning of the warning's passed, the ^gassed,
and flaccid kids are flung a^cross the ^stars.
The psycho^dramas and the traumas gone
the ^songs are left unsung and hung up^on the ^scars.
And then a^long comes Mary, \echo{^Mary, Mary} 
then a^long comes Mary, \echo{^Mary, Mary}
And does she ^want to see the ^stains, 
the dead re^mains of all the ^pains she left the ^night before? ^
Will their waking ^eyes reflect the ^lies, 
and make them ^realize their ^urgent cry for ^sight no more. ^
\endverse

\beginchorus
\[D]When we \[D#]met I was sure out \[D]to \[Cm]lunch,
now my \[D]empty \[G]cup tastes as sweet as \[D]the \[D#]punch, sweet as the \[G G G]punch.
{\nolyrics \[G G G] \[Cm] \[D D D] \[Cm] \[D# D# D#] \[D] \[C C C] \[D] \rep{2}}
\lrep \[D]When we \[D#]met I was sure out \[D]to \[Cm]lunch,
now my \[D]empty \[G]cup tastes as sweet as \[F]the \[B&]punch, \rrep~\rep{6} sweet as the punch.
\endchorus


\endsong
