\beginsong{Always Look on the Bright Side of Life}[
    wuw={Monthy Pyton}, 
    pfii={251}, 
    pfiii={131}, 
    kssiv={162}, 
    index={Some things in life are bad},
]

\beginverse
Some \[Dm]things in life are \[G7]bad, they can \[C]really make you \[Am]mad,
\[F]other things will just \[G7]make you swear and cu\[C]rse. \[(C7)]
When \[F]you're chewing on your life's \[G]gristle: \[C]don't grumble, give \[Am]a whistle
and \[Dm]this'll help things \[D7]turn out for the \[G]best. \[G7]
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]sides of life! \[C](Pf\[Am]ei\[F]fen)\[G] \rep{2}
\endchorus

\beginverse
If ^life seems jolly ^rotten, there's ^something you've for^gotten
and ^that's to laugh and ^smile and dance and ^sing. ^
When ^you're feeling in the ^dupms, ^don't be silly ^chumps
just ^put your lips and ^whistle - that's the ^thing! ^
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]sides of life! \[C](Pf\[Am]ei\[F]fen)\[G] \rep{2}
\endchorus

\beginverse
For ^life is quite ab^surd and ^death's the final ^word,
you must ^always face the ^curtain with a ^bow. ^
For^get about your ^sins, give the ^audience a ^grin.
En^joy it, it's your ^last chance any^how. ^
\endverse

\beginchorus 
So \[C]Always \[Am]look on the \[F]bright \[G]sides of death! \[C](Pf\[Am]ei\[F]fen)\[G]
\[C]Just bef\[Am]ore you \[F]draw your \[G]terminal \[C]breath.(Pf\[Am]ei\[F]fen)\[G]
\endchorus

\beginverse
^Life's a piece of ^shit, ^when you look on ^it,
^life's a laugh and ^death's a joke, it's ^true. ^
You'll ^see it's all a ^show, keep 'em ^laughing as you ^go,
just re^member that the ^last laugh is on ^you. ^
\endverse

\beginchorus
\[C]Always \[Am]look on the \[F]bright \[G]sides of life! \[C](Pf\[Am]ei\[F]fen)\[G] \rep{4}
\[C]
\endchorus

\endsong
