\beginsong{Angie}[
    wuw={Rolling Stones}, 
    pfiii={120}, 
    kssiv={164},
]

\beginverse
\[Am]Angie, \[E]An\[E7]gie, \[G]when will those \[B&]clouds all \[F]disa\[C]ppear?
\[Am]Angie, \[E]An\[E7]gie, \[G]where will it \[B&]lead us \[F]from \[C]here?
\endverse

\beginchorus
With no \[G]loving in our souls and no \[Dm]money in our \[Am]coats
\[C]You can't \[F]say we're satis\[G]fied
\[Am]Angie, \[E]An\[E7]gie, \[G]you can't \[B&]say we \[F]never \[C]tried.
\endchorus

\beginverse
^Angie, you're ^beautiful ^yeah, ^there ain't a ^time we ^say good^bye?
^Angie, I ^still love ^you, ^remember ^all those ^nights you ^cried?
\endverse

\beginchorus
All the \[G]dreams we held so close seemed to \[Dm]all go up in \[Am]smoke
\[C]Let me \[F]whisper in your \[G]ear.
\[Am]Angie, \[E]An\[E7]gie, \[G]where will \[B&]they lead \[F]us from \[C]here?
\endchorus

\beginverse
{\nolyrics \[Am]\[E]\[E7]\[G]\[B&]\[F]\[C]
\[Am]\[E]\[E7]\[G]\[B&]\[F]\[C] }
\endverse

\beginchorus
Oh \[G]Angie, don't you weep, all your \[Dm]kisses ain't that \[Am]sweet
\[C]I hate that \[F]sadness in your \[G]eyes
But \[Am]Angie, \[E]An\[E7]gie, \[G]there ain't a \[B&]time we \[F]say good\[C]bye.
\endchorus

\beginchorus
With no \[G]loving in our souls and no \[Dm]money in our \[Am]coats
\[C]You can't \[F]say we're satis\[G]fied
But \[Dm]Angie, I still love you \[Am]baby
\[Dm]Ev'rywhere I look I see your \[Am]eyes
\[Dm]There ain't a woman that comes \[Am]close to you
\[C]Come on \[F]baby, dry your \[G]eyes
\endchorus

\beginverse
^Angie, ^An^gie, ^ain't it ^good to ^be a^live?
^Angie, ^An^gie, ^you can't ^say we ^never ^tried.
\endverse
\endsong
