\beginsong{Ashes To Ashes}[
	wuw={David Bowie},
	alb={Scary Monsters (And Super Creeps)},
	jahr={1980},
]

\beginverse*
\nolyrics{Intro: \lrep \[Am] \[G] \[Dm] \rrep \rep{4} \[Am]}
\endverse

\beginverse\memorize
\[G] Do you remember a guy that's been\[Em7] in such an early song?
\[C] I've heard a rumour from Ground Control. \[D] Oh no, don't say it's true.
\[F] They got a message from the Action Man,
\[C]I'm happy, \[Em]hope you're happy \[F]too,
I've loved and I've needed \[G]love, sordid de\[E/G#]tails following...
\[A]The shrieking of nothing is killing, just 
\[E] pictures of Jap girls in synthesis and I
\[G] Ain't got no money and I ain't got no \[D]hair,
\[F] but I'm hoping to kick but the planet is \[C]glowing\[Em]...
\endverse

\beginchorus
\[F]Ashes to ashes, \[G]funk to funky, \[C]we know Major \[Am]Tom's a junkie.
\[F]Strung out in heaven's \[G]high hitting an \[Am]all-time \[G]low... \[Dm]
\nolyrics{Interlude: \lrep \[Am] \[G] \[Dm] \rrep \rep{4} \[Am]}
\endchorus

\beginverse
^Time and again I tell myself^ I'll stay clean tonight,
^ but the little green wheels are following ^me... Oh no, not again.
^ I'm stuck with a valuable friend,
^I'm happy, ^hope you're happy ^too.\newpage
One flash of light, ^but no smoking pis^tol.
^ I've never done good things,
^ I've never done bad things,
^ I never did anything out of the ^blue, woh-oh-oh.
^ Want an axe to break the ice,
^wanna come down right ^now.
\endverse

\beginchorus
\[F]Ashes to ashes, \[G]funk to funky, \[C]we know Major \[Am]Tom's a junkie.
\[F]Strung out in heaven's \[G]high hitting an \[Am]all-time \[G]low... \[Dm] \[Am] \[G]
~
\[Dm]My mother said to \[Am]get things done
you'd \[G]better not mess with \[Dm]Major Tom.
\[Am]My mother said to \[G]get things done
you'd \[Dm]better not mess with \[Am]Major Tom.
\[G]My mother said to \[Dm]get things done
you'd \[Am]better not mess with \[G]Major Tom.
\[Dm]My mother said to \[Am]get things done
you'd \[G]better not mess with \[Dm]Major Tom.

\nolyrics{Outro: \lrep \[Am] \[G] \[Dm] \rrep \rep{3} \[Am]}
\endchorus


\endsong
