\beginsong{Black Summer}[
    wuw={Red Hot Chili Peppers}, 
    alb={Unlimited Love}, 
    jahr={2022},
    index={A lazy rain am I, the skies refuse to cry},
]

\begin{minipage}[t]{.85\textwidth}%
\beginverse*\nolyrics
Intro: \[Em] \[Em]
\endverse

\beginverse\memorize
A \[Em]lazy rain am \[G]I, the \[D]skies refuse \[A]to \[Em]cry,
cre\[Am]mation takes its \[Em]piece of your\[D/F#] supp\[G]ly. \[D]
The \[Em]night is dressed like \[G]noon, a \[D]sailor \[A]spoke too \[Em]soon
and \[Am]China's on the \[Em]dark side of \[D/F#]the \[G]moon. \[D] \echo{Hit me now...}
\endverse

\beginverse*\nolyrics
Interlude: \[C] \[G] - \[D] \[E] - \[G] \[A] - \[E]
\endverse
\end{minipage}%
\begin{minipage}[t]{.15\textwidth}
	\vspace{0pt}
    \begin{flushright}
    \hfill\gtab{E/G#}{4:(143121)}
    \end{flushright}
\end{minipage}%

\beginverse
^Platypus are a ^few, the ^secret life ^of ^Roo,
a ^personali^ty I ne^ver ^knew. ^\echo{Get it on...}
My ^crater weighs a ^ton, the ^archers ^on the ^run
and ^no one stands a^lone behind the ^sun. ^ \[E/G#]
\endverse

\beginchorus
It's \[C]been a long \[G]time since I \[D]made a new \[E]friend,
\[G]waitin' on a\[A]nother black \[E]summer to end.
It's \[C]been a long \[G]time and you \[D]never know \[E]when,
\[D]waitin' on a\[A]nother black \[E]summer to end.
\endchorus

\beginverse*\nolyrics
Solo: 
^ - ^ - ^ ^ - ^ - ^ - ^ ^ - ^ - ^
^ - ^ - ^ ^ - ^ - ^ - ^ ^ - ^ - \[G] - \[E/G#] - \[E/G#]
\endverse
% [Guitar Solo]

\beginverse
^Crack the flaming ^whip, a-^sailin' on a cen^sor^ship,
^riding on a headless ^horse to make ^the ^trip... ^
\endverse

\beginchorus
...\[C]been a long \[G]time since I \[D]made a new \[E]friend,
\[G]waitin' on a\[A]nother black \[E]summer to end.
It's \[C]been a long \[G]time and you \[D]never know \[E]when,
\[D]waitin' on a\[A]nother black \[E]summer to end.
~
{\nolyrics \[Em] \[G] \[D] \[Em]}
~
I've been \[Am]waitin', I've been \[Em]waitin',
\[D]Waitin' on another black \[A]summer to end.
I've been \[Em]waitin', I've been \[G]waitin',
\[D]Waitin' on another black \[Em]summer to end.
I've been \[Am]waitin', I've been \[Em]waitin',
\[D]Waitin' on another black \[A]summer to end. \[Em]
\endchorus

\endsong
