\beginsong{Boulevard of Broken Dreams}[
    wuw={Green Day}, 
    alb={American Idiot},
    jahr={2004}, 
    pfiii={138}, 
    index={I walk a lonely road},
]

\beginverse
\[Em]I walk a \[G]lonely road, the \[Dsus2]only one that \[Asus2]I have ever kno\[Em]wn.
Don't know \[G]where it goes, \[Dsus2]but it's home to \[Asus2]me and I walk a\[Em]lone.
\endverse

\beginverse
^I walk this ^empty street ^on the Boule^vard of Broken ^Dreams.
Where the ^city sleeps and ^I'm the only ^one and I walk a^lone.
\endverse

\beginverse*
\[G]\[Dsus2] I walk a\[Asus2]lone, I walk a\[Em]lone, 
\[G]\[Dsus2] I walk a\[Asus2]lone, I walk up...
\endverse

\beginchorus
\[C]My \[G]shadow's the \[Dsus2]only one that \[Asus2]walks beside me,
\[C]My \[G]shallow \[Dsus2]heart's the only \[Asus2]thing that's beating.
\[C]Some\[G]times I \[Dsus2]wish someone out \[Asus2]there will find me.
\[C]Till \[G]then I \[E]walk alone.
\endchorus

\beginverse*
\[Em]Ah-Ah\[G] Ah-Ah\[Dsus2] Ah-Ah \[Asus2]Ahhh-Ah 
\[Em]Ah-Ah\[G] Ah-Ah\[Dsus2] Ah-Ah \[Asus2]
\endverse

\beginverse
^I'm walking ^down the line ^that divides me ^somewhere in my ^mind.
On the ^borderline ^of the edge and ^where I walk a^lone.
\endverse

\beginverse
^Read be^tween the lines of ^what's fucked up and ^everything`s all ^right.
Check my ^vital signs to ^know I'm still a^live and I walk a^lone
\endverse

\beginverse*
\[G]\[Dsus2] I walk a\[Asus2]lone, I walk a\[Em]lone, 
\[G]\[Dsus2] I walk a\[Asus2]lone, I walk up...
\endverse

\printchorus

\beginverse*
\[Em]Ah-Ah\[G] Ah-Ah\[Dsus2] Ah-Ah \[Asus2]Ahhh-Ah 
\[Em]Ah-Ah\[G]\[Dsus2] I walk a\[Asus2]lone, I walk up...
\endverse

\beginverse*
\nolyrics{Solo: \[Em] \[G] \[Dsus2] \[Asus2] \rep{2} }
\endverse

\beginverse
^I walk this ^empty street ^on the Boule^vard of Broken ^Dreams
Where the ^city sleeps and ^I'm the only ^one and I walk a^lone.
\endverse

\printchorus

\endsong
