\beginsong{Can't Stop}[wuw={Red Hot Chili Peppers}, jahr=2003, alb={By the Way}]

\interlude{Intro: \[Am G Em F]}

\beginverse\memorize
\[Am]Can't stop addicted to the shinding, \[G]chop hop I know I'm gonna win big, -- \
\[Em]choose not a life of imitation, \[F]distant cousin' to the reservation. -- \
\[Am]Defunct the pistol that you pay for, \[G]this punk the feeling that you say for, -- \
\[Em]{in time} I want to be your best friend, \[F]Eastside love is living on the westend.

\[Am]Knocked out, but boy you better come to, \[G]don't die you know the truth as some do, -- \
\[Em]{go write} your message on on the pavement \[F]burn so bright I wonder what the wave meant. -- \
\[Am]White heat is screaming in jungle, \[G]compete the motion if you stumble, -- \
\[Em]go ask the dust for any answers, \[F]come back strong with 50 belly dancers!
\endverse

\beginchorus
The \[Am]world I love, the \[G]tears I've dropped, to \[Em]be part of the \[F]wave - can't stop,
\[C]ever wonder \[G]if it's \[Em]all for \[F]you.
The \[Am]world I love, the \[G]trains I hop, to \[Em]be part of the \[F]wave - can't stop,
\[C]Come and tell me \[G]when it's \[Hm]time \[C]to.
\endchorus

\beginverse
^Sweetheart is bleeding in the snowcone, ^so smart she's leading me to ozone,  -- \
^music the great communicator ^use two sticks to make it in the nature.  -- \
^I'll get you into penetration, ^the gender of a generation,  -- \
^the birth of every other nation, ^worth your weight the gold of meditation.
\newpage
^This chapter's going to be a closed one, ^smoke rings, I know you're going to blow one,  -- \
^all on a spaceship persevering, ^use my hands for everything but steering. -- \
^Can't stop the spirits when they need you, ^mop tops are happy when they feed you, -- \
^jay butterfly is in the treetop,  ^birds that blow the meaning into bebop. 
\endverse

% \printchorus

\beginchorus
\[Am]Wait a minute I'm \[G]passing out, win or \[Em]lose, just like \[F]you.
\[Am]Far more shockin' than \[G]anything I ever \[Em]knew, how 'bout \[F]you.
\[Am]Ten more reasons why \[G]I need somebody \[Em]new, just like \[F]you.
\[Am]Far more shockin' than \[G]anything I ever \[Em]knew, right on \[F]cue.
\endchorus

\beginverse
^Can't stop addicted to the shinding, ^chop hop I know I'm gonna win big,  -- \
^choose not a life of imitation, ^distant cousin' to the reservation. -- \
^Defunct the pistol that you pay for, ^this punk the feeling that you say for,  -- \
^in time I want to be your best friend, ^Eastside love is living on the westend. -- \
^Knocked out but boy you better come to, ^don't die you know the truth as some do,  -- \
^go write your message on on the pavement, ^burn so bright I wonder what the wave meant. -- \
^Kick start the golden generator, ^sweet talk but don't intimidate her,  -- \
^can't stop the Gods from engineering, ^feel no need for any interfering. -- \
\[Am]Your  image in the dictionary, \[G]this life is more than ordinary,  -- \
\[Em]can I get two maybe even three of these, \[F]comin' from space to teach you of the Pliedes. -- \
\[Am]Can't stop the spirits when they need you, this life is more than just a read-through.
\endverse

\endsong
