\beginsong{Cathedral}[
    wuw={Crosby, Stills and Nash},
    alb={CSN},
    jahr={1977}, 
    index={Six o'clock in the morning},
]

\beginverse
\[Em]Six o' clock in the morning,
I feel \[D]pretty good \[A]
so I dropped in\[Am]to the luxury of the Lords. \[Asus4] \[Am]
Fighting dragons and crossing swords,\[Asus4] \[Am]
with the people against the hordes
who \[Em]came to conquer. \[D] \[A]
\endverse

\beginverse
^Seven o'clock in the morning,
^here it comes, I ^taste the warning.
And I am ^so amazed I'm here today, ^ ^ 
seeing things so clear this way ^ ^
in the car and on my way
to ^Stonehenge ^ ^
\endverse

\beginchorus
\[Em]I'm flying in Win\[D]chester Ca\[A]thedral, \[Em]
sunlight pouring through the \[D]break of da\[A]y \[Em]
Stumbled through the door and \[D]into the chamber. \[A]
There's a \[Am]lady setting flowers on a table covered lace
and a \[Am]cleaner in the distance finds a cobweb on a face
and a \[Am]feeling deep inside of me tells me
\[Am]this can't be the \[Em]place. \[D] \[A]
\endchorus

\beginchorus
\[Em] I'm flying in Win\[D]chester Ca\[A]thedral. \[Em]
All religion has to \[D]have its da\[A]y. \[Em]
Expressions on the \[D]face of the Saviour \[A]
made me \[Am]say: 'I can't \[Am]stay.'
\endchorus

\beginverse*
Bridge:
\[Em]Open up the gates of the church and let me \[D]out of here.
Too many \[Em]people have lied in the name of Christ, for \[D]anyone to heed the call.
So many \[Em]people have died in the name of Christ, that I \[D]can't believe it all.\newline

And now I'm \[Am]standing on the grave of a soldier that died in 1799. \[Asus4] \[Am]
And the day he died it was a birthday and I noticed it was mine.  \[Asus4] \[Am]
And my head didn't know just who I was and I went spinning back in time. 
And I am \[Em]high upon the \[D]altar,
\[Em]high upon the \[D]altar, \[Am]high.
\endverse

\beginchorus
\[Em]I'm flying in Win\[D]chester Ca\[A]thedral. \[Em]
It's hard enough to \[D]drink the \[A]wine. \[Em]
The air inside just \[D]hangs in delusion. \[A]
But given \[Am]time\[Asus4]\[Am], I'll be fine. \[Em]
\endchorus

\endsong
