\beginsong{Dear Mr. President}[
    wuw={Pink},
]

\beginverse
{\nolyrics Intro: \[G] \[D/f#] \[Em] \[D/f#]}

\[G]Dear Mr President, \[D/f#]come take a walk with me. \[Em] \[D/f#]
Lets pretend, \[G]we're just two people and, \[D/f#]you're not better than me,
I'd like to, \[Em]ask you some questions if we could, \[D/f#]speak honestly.

\[C]What do you \[Am]feel when you see the \[G]homeless on the street?\[D/f#]
\[C]Who do you \[Am]pray for at night be\[G]fore you go to sleep?\[D/f#]
\[C]What do you \[Am]see when you look in the \[Em]mirror?\[D/f#]
Are you pro\[Cadd9]ud?
\endverse

\beginchorus
How do you \[G]sleep while the \[D/f#]rest of us\[Am] cry? \[C]
How do you \[G]dream when a \[D/f#]mother has no \[Am]chance to say goodbye?\[C]
How do you \[G]walk with your he\[D/f#]ad held \[Am]high?  \[C]
Can you even \[Em]look me \[D/f#]in the eye?\[Cadd9]
And tell me why!
\endchorus
\beginverse*
{\nolyrics Zwischenspiel: \[G] \[D/f#] \[Em] \[D/f#]}
\endverse

\beginverse
^Dear Mr president, ^were you a lonley boy? \echo{Were you a lonley boy?}
^Are you a lonely boy? \echo{Are you a lonely ^boy?}
How can you say, ^no child is left behind^
we're not dumb, and we're not bl^ind \echo{We're not blind}
\endverse

\beginverse*
They're all sitting in your cells
\[D/f#]while you pave the road to hell.
\[C]What kind of \[Am]father might take his own \[G]daughter's right away?\[D/f#]
\[C]And what kind of \[Am]father might hate his own \[G]daughter if she were gay?\[D/f#]
\[C]I can only i\[Am]magine what the first \[Em]lady has to \[D/f#]say
you've come a \[Cadd9]long way, from whiskey and cocaine.
\endverse

\beginchorus
\endchorus

\beginverse*
Let me tell you 'bout \[Em]hard work, \[D/f#] \[G]
minimum \[Am]wage with a baby on the \[C]way.
Let me tell you 'bout \[Em]hard work, \[D/f#] \[G]
re-building your \[Am]house after the bombs took them a\[C]way.
Let me tell you 'bout \[Em]hard work, \[D/f#] \[G]
building a \[Am]bed out of a cardboard \[C]box.
Let me tell you 'bout \[Em]hard work, \[D/f#]h\[G]ard work, h\[Am]ard wor\[C]k,
you don't know nothing 'bout \[Em]hard work, \[D/f#]h\[G]ard work,
\[Am]hard w\[Cadd9]ork!

\[G]How do you sleep \[D/f#]at night?
\[Em]How do you walk, \[D/f#]with your head held \[G]high?
\endverse

\beginverse
^Dear Mr president ^you'd never take a walk with me. ^  ^
Hmmm. Would you? \[G]
\endverse
\endsong

\begin{intersong}
\end{intersong}