\beginsong{The Diary of Jane}[
    wuw={Breaking Benjamin}, 
	alb={Phobia},
    jahr={2006},
    index={If I had to, I would put myself right beside you},
]

\beginverse*
\nolyrics Intro: \[Am] \[Am] \[F] \rep{2}
\endverse

\beginverse\memorize
If I \[Am]had to, I would put myself right be\[Am]side you.
So let me ask, would you \[F]like that? Would you \[G]like that?
And I \[Am]don't mind, if you say this love is the \[Am]last time.
So now I'll ask, do you \[F]like that? Do you \[G]like that? \echo{No!}
\endverse

\beginchorus
\[Am]Something's getting in the \[F]way, something's just about to \[C]break.
I will try to find my \[G/H]place in the diary of \[F]Jane,
so tell me \[G]how it should \[Am]be. \[Am] \[F]
\endchorus

\beginverse
Try to ^find out what makes you tick as I ^lie down
sore and sick, do you ^like that? Do you ^like that?
There's a ^fine line between love and hate and I ^don't mind
Just let me say that I ^like that, I ^like that.
\endverse

\beginchorus
\[Am]Something's getting in the \[F]way, something's just about to \[C]break.
I will try to find my \[G/H]place in the diary of \[Am]Jane.
As I burn another page,\[F] as I look the other \[C]way,
I still try to find my \[G/H]place in the diary of \[F]Jane,
so tell me \[G]how it should \[Am]be. \newpage
\textnote{\bfseries Bridge}
\[C]Desperate, I will crawl, \[Dsus2]waiting for so long:
\[Am]No love, there is no love.
\[C]Die for anyone, \[Dsus2]what have \[F]I be\[E]come?!
\endchorus

\beginchorus
\[Am]Something's getting in the \[F]way, something's just about to \[C]break.
I will try to find my \[G/H]place in the diary of \[Am]Jane.
As I burn another page,\[F] as I look the other \[C]way,
I still try to find my \[G/H]place in the diary of \[Am]Jane. \[Am] \[Am]
\endchorus


\endsong

