\beginsong{Don't look back in anger}[wuw={Oasis}, pfiii={145}, index={Slip inside the eye of your mind}]

\beginverse
\[C]Slip inside the \[G]eye of your \[Am]mind,
don't you \[E]know you might \[F]find,
\[G] a better place to \[C]play. \[Am]\[G]
\[C]You said that \[G]you'd never \[Am]been,
but all the \[E]things that you've \[F]seen,
\[G] slowly fade a\[C]way. \[Am]\[G]
\endverse

\beginverse*
\[F] So I start a revo\[Fm]lution from my \[C]bed.
'Cos you \[F]said the brains I \[Fm]had went to my \[C]head.
\[F]Step outside, the \[Fm]summertime's in \[C]bloom.
\[G]Stand up beside the fireplace!
\[E7]Take that look from off your face!
'Cos \[Am]you ain't ever \[G]gonna burn my \[F]heart ouu\[G]uuuuuuuuuuuuuut.
\endverse

\beginchorus
\[C]So \[G]Sally can \[Am]wait, she \[E]knows it's too \[F]late
as we're \[G]walking on \[C]by. \[Am]\[G]
Her \[C]soul \[G]slides a\[Am]way, \[E7] but don't look \[F]back in anger \[G]
I heard you \[C]say. \[G] \[Am] \[E] \[F] \[G] \[C] \[Am]\[G]
\endchorus

\beginverse
^Take me to the ^place where you ^go
where ^nobody ^knows, ^if it's night or ^day. ^^
^Please don't put your ^life in the ^hands
of a ^rock and roll ^band, ^who'll throw it all a^way. ^^
\endverse

\beginverse*
\[F] So I start a revo\[Fm]lution from my \[C]bed.
'Cos you \[F]said the brains I \[Fm]had went to my \[C]head.
\[F]Step outside, the \[Fm]summertime's in \[C]bloom!
\[G]Stand up beside the fireplace!
\[E7]Take that look from off your face!
'Cos \[Am]you ain't ever \[G]gonna burn my \[F]heart ouu\[G]uuuuuuuuuuuuuut
\endverse

\beginchorus
\endchorus

\beginverse*
Her \[C]soul \[G]slides a\[Am]way.
But don't look \[F]back in anger.
Don't look \[Fm]back in anger.
I heard you \[C]say \[G] \[Am] \[E] \[F] \[G] at least not to\[C]day.
\endverse

\endsong
