\beginsong{Dumb Ways to Die}[wuw={Tangerine Kitty}, jahr=2012]

\beginverse\memorize
Set \[C]fire \[F]to your \[C]hair. \[F]
Poke a \[C]stick at a \[F]grizzly \[C]bear. \[F]
Eat \[C]medi\[F]cine that is \[C]out of \[F]date.
Use your \[C]private \[F]parts as pi\[C]ranha \[F]bait.
\endverse

\beginchorus
\[C]Dumb \[G]ways to \[Am]die, \[Em] so \[F]many dumb \[D7]ways to \[G]die.
\[C]Dumb \[G]ways to \[Am]die, \[Em] so \[F]many dumb \[G]ways to \[C]die.
\endchorus

\beginverse
Get your ^toast out ^with a ^fork. ^
Do your ^own e^lectrical ^work. ^
^Teach your^self ^how to ^fly.
And Eat a ^two week ^old unre^frigerated ^pie...
\endverse

\printchorus

\beginverse
Invite a ^psycho ^killer in^side. ^
Scratch a ^drug dealer’s^ ^brand new ^ride.
Take your ^helmet ^off in ^outer-^space.
Use a ^clothes dryer ^as a ^hiding ^place.
\endverse

\printchorus

\beginverse
Keep a ^rattle ^snake as a ^pet. ^
Sell ^both your kidneys ^on the ^inter^net.
^Eat a ^tube of ^super-^glue 
^I wonder: what's this red button do?
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[F]Dress up \[G]like a \[C]moose during \[Am]hunting \[F]season...
\[F]Disturb a \[G]nest \[C]of wasps for \[Am]no good reason...
\[G]Stand on the edge of a \[Am]train station platform.
\[G]Drive around the boom gates at a \[Am]level crossing.
\[F]Run across the \[G]tracks between the \[Am]platforms .
\[F]They may not rhyme but their\[G] quite possibly.
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\[C]The \[G]dumbest \[Am]ways to die,\[Em] the \[F]dumbest \[D7]ways to \[G]die
The \[C]dumbest \[G]ways to \[Am]di-i-i-ie.... 
So \[Em]many dumb ways... so \[G]many dumb ways to \[C]die!
\endchorus

\endsong

