\beginsong{Enter Sandmann}[wuw={Metallica}, index={Say your prayers little one}, alb={Metallica}, jahr=1991]

\renewcommand{\everychorus}{\textnote{\bf Intro}}
\beginchorus
\nolyrics
\textbf{2x} Intro Acoustic: \[Em Em Em Em]
\textbf{6x} with Metal-Guitar: \[Em Em Em Em]
\textbf{2x} full band: \[Em Em Em G--F#--F#--G--F#--Em]
\endchorus

\beginverse
\[Em] Say your prayers litt\[F]le \[Em]one
Don't forget, \[F]my \[Em]son, to include every\[G--F#--F#--G--F#--Em]one.
\[Em] Tuck you in, warm \[F]with\[Em]in,
keep you free \[F]from \[Em]sin, 'till the sandman he \[G--F#--F#--G--F#]comes.
\[F#]Sleep with \[F#]one eye open,\[F#] gripping your \[F#]pillow tight.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[F#]Exit, light. \[F#]Enter, \[Em]night.
\[F#]Take my \[Em]hand, we're \[Em]off to never-never land. \[Em]
\endchorus

\beginverse
\[Em] Somethings wrong, shut \[F]the \[Em]light,
heavy thoughts \[F]to\[Em]night and they aren't of snow \[G--F#--F#--G--F#--Em]white.
\[] Dreams of war, dreams \[F]of \[Em]liars, 
dreams of dra\[F]gon's \[Em]fire, and of things that will \[G--F#--F#--G--F#--Em]bite.
\[F#]Sleep with \[F#]one eye open,\[F#] gripping your \[F#]pillow tight.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[F#]Exit, light. \[F#]Enter, \[Em]night.
\[F#]Take my \[Em]hand, we're \[Em]off to never-never land. \[Em]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Solo}}
\beginchorus
\nolyrics
\[Em Em Em G--F#--F#--G--F#--Em] \rep{2}
\[F# F# F# F#--Em] ~~~~~ \[F# F# F# Em] ~~~~~ \[F# Em]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge / Prayer}}
\beginchorus
\[Em] Now I lay me down to sleep, \echo{Now I lay me down to sleep,}
\[Em] pray the Lord my soul to keep, \echo{pray the Lord my soul to keep,}
\[Em] If I die before I wake, \echo{If I die before I wake,}
\[Em] pray the lord my soul to take. \echo{pray the lord my soul to take.}
~
\[F#] Hush little baby, don't say a word,
\[F#] And never mind that noise you heard,
\[F#] It's just the beasts under your bed,
\[F#] In your closet, in your head!
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[F#]Exit, light. \[F#]Enter, \[Em]night. \[F#]Grain of \[Em]sand...
\[F#]Exit, light. \[F#]Enter, \[Em]night.
\[F#]Take my \[Em]hand, we're \[Em]off to never-never land. \[Em]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Outro}}
\beginchorus
\begin{nolyrics}Riff-Only: \[Em Em]\end{nolyrics}
\[Em Em]Booo! Yeah-\[Em Em]yeahhh! \[Em] \[G--F#--F#--G--F#--]{Nooo-no.} 
Acoustic: \[Em Em Em] \lrep We're \[Em]off to never-never land. \echo{\[Em]Take my \[Em]hand!} \[Em] \rrep ~\rep{4}
\endchorus

\endsong
