\beginsong{Father and Son}[wuw={Cat Stevens}, pfii={235}, pfiii={124}, gruen={168}, kssiv={178}, siru={140}, index={It's not time to make a change}]

\beginverse
\echo{Father} It's not \[G]time to make a \[D]change, just re\[C]lax and take it \[Am7]easy.
You're still \[G]young that's your \[Em]fault
there's so \[Am]much you have to \[D]know.
Find a \[G]girl, settle \[D]down, if you \[C]want to, you can \[Am7]marry.
Look at \[G]me, I am \[Em]old, but I'm \[Am]happy. \[C]\[D]
I was \[G]once like you are \[Hm7]now, and I \[C]know that its not \[Am]easy
to be \[G]calm, when you've \[Em]found something going \[Am]on. \[C]\[D]
But take your \[G]time, think a l\[Hm7]ot, think of \[C]everything you've \[Am7]got
For you will \[G]still be here to\[Em]morrow, but your \[D]dreams may \[G]not
\endverse
\beginverse*
{\nolyrics Zwischenspiel: \[C] \[G]}
\endverse
\beginverse
\echo{Son} How can \[G]I try to ex\[Hm]plain?  When I \[C]do he turns a\[Am]way again;
it's \[G]always been the \[Em]same, same old \[Am]story. \[C]\[G]
From the \[G]moment I could \[Hm]talk I was \[C]ordered to \[Am7]listen
now there's a \[G]way and I \[Em]know that I \[D]have to go a\[G]way
I \[D]know I \[C]have to \[G]go.
\endverse

\beginverse*
{\nolyrics Zwischenspiel: \[C] \[G]}
\endverse

\beginverse
\echo{Father} It's not \[G]time to make a \[D]change, just sit \[C]down, take it \[Am7]slowly.
You're still \[G]young, that's your \[Em]fault, 
there's so \[Am]much you have to go \[D]through.
Find a \[G]girl, settle \[D]down, if you \[C]want to you can \[Am7]marry.
Look at \[G]me, I am \[Em]old, but I'm \[Am]happy. \[C]\[D]
\endverse

\beginverse
\echo{Son} All the \[G]times that I \[Hm]cried, keeping \[C]all the things I \[Am]knew inside.
It's \[G]hard, but it's \[Em]harder to ig\[Am]nore it. \[C]\[D]
If they were \[G]right, I'd a\[Hm]gree, but it's \[C]them they know, not \[Am]me.
Now there's a \[G]way, and I \[Em]know that I \[D]have to go a\[G]way.
I \[D]know I \[C]have to \[G]go
\endverse

\endsong
