\beginsong{Festival Lights}[
    wuw={The McCalmans}, 
    alb={Festival Lights}, 
    jahr={1995}, 
    index={The Folks out here are kind},
]
\beginverse*
\[D] \[G] \[D]
\endverse

\beginverse\memorize
\[A]The folks out here are \[D]kind,\[G] they let me \[A]sleep all \[D]day,
\[G]they don't\[A] seem to \[D]mind,\[Hm] I'm \[G]dreaming my life a\[Em]way. \[A]
There's \[A7]traffic jams near the \[D]Hague,\[G] we'll have to \[A]leave here \[D]soon,
\[G]sing our \[A]songs and \[D]go,\[Hm] to the \[G]light of a lowland \[Em]moon. \[A]
\endverse

\beginchorus
And it \[D]seems like I'll miss \[G]Autumn in \[A]Edinburgh,
\[D]that's the one I should have \[G]spent with \[A]you.
With the \[D]rain lashing down, a \[G]fog on the \[A]Meadows,
as the \[D]festival lights, as the \[G]festival \[A]lights go \[D]dim. \[G] \[D] \[G]
\endchorus

\beginverse
Been ^wandering round this ^town, ^trying to ^pass some ^time,
^it seems I ^know these ^streets^ as ^well as I know ^mine. ^
The ^clock has turned to ^five,^ perhaps you'll ^soon be ^home,
^I'll call and^ say I'm ^missing ^you, and ^then hang up the ^phone. ^
\endverse

\printchorus

\beginverse*
\[A]Everybody's written a \[Em]song, which says
You've \[D]been on the road, \[G]been on the \[D]road so \[Em]long. \[A]
\endverse

\beginverse
% ^The Folks out here are ^kind,^ they let me ^sleep all ^day,
% ^they don't^ seem to ^mind,^ I'm ^dreaming my life a^way. ^
% There's ^traffic jams near the ^Hague,^ we'll have to ^leave here ^soon,
% ^sing our ^songs and ^go,^ to the ^light of a lowland ^moon. ^
wie 1.
\endverse

\printchorus

\beginverse*
\[A]Everybody's written a \[Em]song, which says
you've \[D]been on the road, \[G]been on the \[D]road so \[Em]long. \[A]
As the \[D]festival lights, as the \[G]festival \[A]lights go \[D]dim. \[G] \[D] \[G] \[D]
\endverse

\endsong
