\beginsong{Hallelujah}[
    wuw={HAIM}, 
    alb={Women in Music Pt. III}, 
    jahr={2020}, 
]

\beginverse*
{\nolyrics Intro: \[C/G]}
\endverse

\beginverse\memorize
\[Am] I met two \[D/F#]angels but \[G]they were in dis\[C]guise,
\[Am] took one \[G/H]look to rea\[C]lize.
\[Am] Tell 'em \[D/F#]anything and \[G]they will sympa\[C]thize,
\[Am] these \[G/H]arms hold \[C]me tight.
\[Am] Old \[D/F#]fears, helped to \[G]ease them in my \[C]mind.
\[Am] New \[D/F#]tears say that \[G]they will dry in \[C]time.
\endverse

\beginchorus
\[Am] Why \[D/F#]me? How'd I \[G]get this halle\[C]lujah?
Halle\[G]lujah
\endchorus

\beginverse
^ Laughing to^gether like our ^thoughts are harmo^nized,
^ been that ^way since '9^5.
^ Give me di^rection when ^it is hard to ^fight,
^ three ^roads, one ^light.
^ Now and ^then I can ^lean my back to ^yours,
^ trave^lin' like our ^feet don't touch the ^floor.
\endverse

\beginchorus
\[Am] Why \[D/F#]me? How'd I \[G]get this halle\[C]lujah?
Halle\[Em]lu\[D/C]jah, halle\[C]lu\[Em]j\[D/C]ah
Why \[C]me? How'd I \[Em]get this halle\[F]l\[Am]u...
\endchorus

\beginverse
^ I had a ^best friend but ^she has come to ^pass,
^ one I ^wish I could ^see now.
^ You always re^mind me that ^memories will ^last,
^ these ^arms reach^ out.
^ You were ^there to pro^tect me like a ^shield,
^ long ^hair running ^with me through the ^field,
\[Am] every\[D/F#]where you've been \[G]with me all a\[C]long.
\endverse

\beginchorus
\[Am]Why \[D/F#]me? How'd I \[G]get this halle\[C]lujah?
\[Am]Why \[D/F#]me? How'd I \[G]get this halle\[C]lujah?
\[Am]Why \[D/F#]me? How'd I \[G]get this halle\[C]lujah?
Halle\[C/G]lujah.
\endchorus

\endsong
