\beginsong{Hallelujah}[wuw={Jeff Buckley}, index={I heard there was a secret chord}, kssiv={180}, biest={566}]

\beginverse*
{\nolyrics Intro: \[C] \[Am] \[C] \[Am]}
\endverse
\beginverse\memorize
I've \[C]heard there was a \[Am]secret chord,
that \[C]David played and it \[Am]pleased the Lord,
but \[F]you don't really \[G]care for music, \[C]do you?\[G] 
Well it \[C]goes like this the \[F]fourth, the \[G]fifth,
the \[Am]minor fall and the \[F]major lift,
the \[G]baffled king com\[Em]posing halle\[Am]lujah.
\endverse

\beginchorus
Halle\[F]lujah, halle\[Am]lujah, halle\[F]lujah, halle\[C]lu-u-\[G]u-u-\[C]jah. \[Am] \[C] \[Am] \[C]
\endchorus

\beginverse
Well your ^faith was strong but you ^needed proof.
You ^saw her bathing ^on the roof.
Her ^beauty and the ^moonlight over^threw you. ^
She ^tied you to her ^kitchen ^chair.
She ^broke your throne and she ^cut your hair.
And ^from your lips she ^drew the halle^lujah.
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse
^Baby I've been ^here before.
I've ^seen this room and I've ^walked this floor.
I ^used to live a^lone before I ^knew you. ^\newpage
I've ^seen your flag on the ^marble ^arch.
But ^love is not a ^victory march,
it's a ^cold and it's a ^broken halle^lujah.
\endverse

\beginchorus
\endchorus

\beginverse
Well ^there was a time when you ^let me know,
what's ^really going ^on below.
But ^now you never ^show that to me ^do you. ^
But re^member when I ^moved in ^you
and the ^holy dove was ^moving, too.
And ^every breath we ^drew was halle^lujah.
\endverse

\beginchorus
\endchorus

\beginverse
Well, ^maybe there's a ^God above.
But ^all I've ever ^learned from love,
was ^how to shoot some^body who out^drew you. ^
It's ^not a cry that you ^hear at ^night.
It's ^not somebody who's ^seen the light.
It's a ^cold and it's a ^broken halle^lujah.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (x2)}}
\beginchorus
{\nolyrics \echo{Ende auf \[C] }}
\endchorus

\endsong
