\beginsong{Hero of War}[wuw={Rise Against}, jahr=2008, alb={Appeal to Reason}]

\beginverse\memorize
He said ''\[C]Son, have you seen the \[Em]world? 
Well, what would you \[F]say, if I said that you \[C]could? 
Just carry this \[F]gun, you'll even get \[C]paid.''
I said ''That sounds pretty \[G]good.''
\endverse

\beginverse
Black leather ^boots, spit-shined, so ^bright. 
They cut off my ^hair, but it looks ^alright. 
We marched and we ^sang, we all became ^friends, 
as we learned how to ^fight.
\endverse

\beginchorus
A hero of \[Am]war! Yeah, that's what I'll \[F]be. 
And when I come \[C]home, they'll be damn proud of \[G]me. 
I'll carry this \[Am]flag to the  grave, if I \[F]must. 
'Cause it's a flag that I \[C]love and a flag that  I \[G]trust.
\endchorus

\beginverse
I kicked in the ^door, I yelled my ^commands. 
The children, they ^cried, but I got my ^man. 
We took him ^away, a bag over his ^face, 
from his family and his ^friends.
\endverse

\beginverse
They took off his ^clothes, they pissed in his ^hands. 
I told them to ^stop, but then, I joined ^in. 
We beat him with ^guns and batons, not just ^once, 
but again and ^again.
\endverse

\printchorus

% \beginchorus
% A hero of ^war!
% Yeah, that's what I'll ^be.
% And when I come ^home,
% they'll be damn proud of ^me.
% I'll carry this ^flag
% to the  grave, if I ^must.
% 'Cause it's a flag that I ^love
% and a flag that I ^trust.
% \endchorus

\beginverse
She ^walked through bullets and ^haze. 
I asked her to ^stop, I begged her to ^stay. 
But she pressed ^on, so I lifted my ^gun 
and I fired ^away..	.
\endverse

\beginverse
And the ^shells jumped through the ^smoke. 
And into the ^sand, that the blood now had ^soaked, 
she ^collapsed, with a flag in her ^hand. 
A flag white as ^snow.
\endverse

\printchorus

% \beginchorus
% A hero of ^war!
% Is that what they ^see?
% Just medals and ^scars?
% So damn proud of ^me.
% And I brought home that flag.
% Now it gathers ^dust.
% But it's a flag that I ^love.
% It's the only flag I ^trust.
% \endchorus

\beginverse
^He said ''Son, have you seen the ^world? 
Well, what would you ^say, if I said that you ^could?''
\endverse


\endsong

\begin{intersong}

\end{intersong}