\beginsong{Heroes}[
    wuw={David Bowie}, 
    alb={Heroes}, 
    jahr={1977}, 
    index={I will be king},
]

\beginverse\memorize
{\nolyrics Intro: \lrep \[D] \[G] \[D] \[G] \rrep}
\[D]I, I will be \[G]king and \[D]you, you will be \[G]queen.
Though \[C]nothing, will drive them a\[D]way,
we can \[Am]beat them,\[Em] just for one \[D]day,
we can be \[C]heroes,\[G] just for one \[D]day.
\endverse

\beginverse
And ^you, you can be ^mean, and ^I, I'll drink all the ^time.
'Cause we're ^lovers, and that is a ^fact, yes we're ^lovers, and that is ^that.
Though ^nothing, will keep us to^gether,
we could steal ^time,^ just for one ^day,
we can be ^heroes,^ forever and ^ever. What d'you say?
\endverse

% 1/2 Strophe instrumental

\beginverse
{\nolyrics Zwischenspiel: \lrep ^ ^ ^ ^ \rrep}
^I, I wish you could ^swim, like the ^dolphins, like dolphins can ^swim.
Though ^nothing, nothing will keep us to^gether,
we can ^beat them,^ forever and ^ever,
oh we can be ^heroes,^ just for one ^day.
\endverse

% 1/2 Strophe instrumental

\beginverse
{\nolyrics Zwischenspiel: \lrep ^ ^ ^ ^ \rrep}
^I, I will be ^king, and ^you, you will be ^queen,
though ^nothing, will drive them a^way.
We can be ^heroes,^ just for one ^day,
we can ^be us,^ just for one ^day.
\endverse

\beginverse
^I, I can re^member \echo{I remember} ^standing, by the ^wall \echo{by the wall}
and the ^guns, shot a^bove our heads, \echo{over our heads}
and we ^kissed, as though nothing could ^fall. \echo{nothing could fall}
And the ^shame, was on the ^other side,
oh we can ^beat them,^ forever and ^ever.
Then we could be ^heroes,^ just for one ^day.
\endverse

\beginverse
^ We can be ^heroes,^ we can be ^heroes,
^ we can be ^heroes, just for one ^day,
we can be ^heroes.
We're ^nothing, and nothing will ^help us,
maybe we're ^lying,^ then you better not ^stay,
but we could be ^safer,^ just for one ^day
Oh-oh-oh-ohh, oh-oh-oh-ohh, just for one day.
\endverse

\endsong
