\beginsong{Hey Jude}[wuw={The Beatles}, jahr={1968}]

\beginverse
Hey \[D]Jude, don’t make it \[A]bad, take a \[A7]sad song and make it \[D]better,
re\[G]member to let her into your \[D]heart, then you can \[A]start to \[A7]make it bet\[D]ter.
\endverse
\beginverse
Hey ^Jude, don’t be a^fraid, you were ^made to go out and ^get her,
the ^minute you let her under your ^skin, then you be^gin to ^make it ^better.
\endverse

\beginchorus
\[D7] And anytime you feel the \[G]pain, 
hey \[Hm]Jude, re\[Em]frain, don’t \[A7]carry the \[D]world upon your shoulders 
\[D7] For well you know that it's a \[G]fool, 
who \[Hm]plays it \[Em]cool by making his \[A7]world a little \[D]colder, 
na-na-na, \[D7]Na-na, \[A7]Na-na-na-na.
\endchorus

\beginverse
Hey ^Jude, don’t let me ^down, you have ^found her, now go and ^get her,
re^member to let her into your ^heart, then you can ^start to ^make it ^better.
\endverse

\beginchorus
\[D7] So let it out and let it \[G]in, 
hey \[Hm]Jude, be\[Em]gin, you're waiting for \[A7]someone to per\[D]form with,
\[D7] and don’t you know that it's just \[G]you, 
hey \[Hm]Jude, you'll \[Em]do, the movement you \[A7]need is on your \[D]shoulders, 
na-na-na, \[D7]Na-na, \[A7]Na-na-na-na.
\endchorus

\beginverse
Hey ^Jude, don’t make it ^bad, take a ^sad song and make it ^better
Re^member you let her under your ^skin, then you be^gin to ^make it 
^better, better, better, better, better, better, woah!
\endverse

\renewcommand{\everychorus}{\textnote{\bf Finé}}
\beginchorus
\lrep \[D]Na, na na \[C]na-na-na-na, \[G]na-na-na-na, hey \[D]Jude! \rrep ~ \rep{8} 
\endchorus

\endsong

\beginscripture{}
Wie zu Beatles-Zeiten üblich, wurde der Song vom Komponistenduo Lennon/McCartney zugeschrieben, obwohl Paul McCartney den größten Anteil an der Komposition dieser Single hatte. Mit 7,5 Millionen verkauften Exemplaren gilt ''Hey Jude'' als erfolgreichste Single der Band.
\endscripture
