\beginsong{Hymn}[wuw={Barclay James Harvest}, alb={Gone to Earth}, jahr={1977}, pfii={203}, pfiii={107}, kssiv={224}, index={Valley's Deep}]

\beginverse
{\nolyrics Intro: \[E]\[Esus4]\[E]}
\[E] Valleys deep and the \[A]mountains so \[E]high,
if you \[A]wanna see God you've got to move on the other \[E]side. \[Esus4]
\[E] You stand up there with your \[A]head in the \[E]clouds,
don't \[A]try to fly you know you might not come \[E]down.
Don't \[A]try to fly, dear God, you might not come \[E]down. \[Esus4]
\endverse

\beginverse
{\nolyrics Zwischenspiel: ^ ^ ^}
^ Jesus came down from ^heaven to ^earth,
the ^people said it was a virgin ^birth. ^
^ Jesus came down from ^heaven to ^earth, 
the ^people said it was a virgin ^birth. 
The ^people said it was a virgin ^birth. ^
\endverse

\beginverse
{\nolyrics Zwischenspiel: ^ ^ ^}
^ He told great stories ^of the ^Lord 
and ^said he was the saviour of us ^all. ^
^ He told great stories ^of the ^Lord 
and ^said he was the saviour of us ^all. 
And ^said he was the saviour of us ^all. ^
\endverse

\beginverse
{\nolyrics Zwischenspiel: ^ ^ ^}
^ For this we killed him ^nailed him up ^high,
he ^rose again as if to ask us ^why.
^ Then he ascended ^into the ^sky,
as ^if to say in God alone we ^soar. 
As ^if to say in God alone we ^fly. ^
\endverse

\beginverse
{\nolyrics Zwischenspiel: ^ ^ ^}
^ Valley's deep and the ^mountains so ^high,
if you ^wanna see God you've got to move on the other ^side. ^
^ You stand up there with your ^head in the ^clouds,
don't ^try to fly you know you might not come ^down.
Don't ^try to fly, dear God, you might not come ^down. ^ \[E]
\endverse

\endsong
