\beginsong{I Don't Want To Miss A Thing}[wuw={Aerosmith}, alb={I Don't Want To Miss A Thing}, jahr={1998}, kssiv={266}]

\beginverse
I could \[D]stay awake \[A]just to hear you \[Hm]breathing
watch you \[G]smile while you are \[D]sleeping while your \[Em]far away dreaming.
I could \[D]spend my life \[A]in this sweet \[Hm]surrender.
I could \[G]stay lost in this \[D]moment \[Em]forever.
Every moment \[F#m]spent with \[Gmaj7]{you is a} moment I \[A7sus4]treasure
\endverse

\beginchorus
\[D]{I don't} want to \[A]close my eyes, \[Em]{I don't} want to fall asleep,
'cause I'd \[G]miss you baby and I \[A]don't want to miss a \[D]thing.
'Cause even when I \[A]dream of you \[Em]the sweetest dream will never do, 
I'd still \[G]miss you baby and I \[G]don't want to \[A]miss a \[D]thing. \[A] \[G]
\endchorus

\beginverse
Lying ^close to you, ^feeling your heart ^beating,
and I'm ^wondering what you're ^dreaming,
wondering ^if it's me you're seeing?
Then I ^kiss your eyes and ^thank God we're ^together.
I just want to ^stay with ^you in this moment for^ever, forever and ever...
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
I don't want to \[C]miss one smile, I don't want to \[G]miss one kiss,
I just want to \[B&]be with you right here with you \[F]just like this.
I just want to \[C]hold you close, feel your heart so \[G]close to mine
and just \[Dm]stay here in this moment for all the \[A]rest of time, yeah, yeah, yeah...
\endchorus

% \printchorus

\endsong
