\beginsong{I don't like mondays}[wuw={Boomtown Rats}, pfii={248}, pfiii={127}, index={The silicon chip inside her head}]

\markboth{\songtitle}{\songtitle}
\beginverse*
{\nolyrics Intro: \[C] \[Em] \[F] \[G] \[F]}
\endverse
\beginverse\memorize
The \[C]silicon chip in\[Em]side her head gets \[F]switched to over\[G]load,
and \[C]nobody’s gonna go to \[Em]school today, he’s gonna \[F]make them stay at \[G]home,
and \[F]daddy doesn’t under\[G]stand it, he always \[C]said she was good as \[F]gold,
and he can \[F]see no reasons, 'cause there \[F]are no reasons.
What \[F]reason do you need to be \[G]show-\[G6]ow-\[G7]ow-\[G6]ow-\[G]own?
\endverse

\beginchorus
\echo{Tell me \[C]why} I don’t like \[Em]Mondays. \echo{Tell me \[F]why} I don’t like \[G]Mondays.
\echo{Tell me \[C]why} I don’t like \[Em]Mondays. I wanna \[F]shoo-oo-woo-woo-woo-\[G]oot
the whole day \[C]down. \[Em] \[F] \[G] \[F] 
\endchorus

\beginverse
The ^Telex machine is ^kept so clean and it ^types to a waiting ^world.
And ^mother feels so shocked, father’s ^world is rocked and their ^thoughts turn to their ^own little girl.
^Sweet 16 ain’t that ^peachy keen, well that ^ain’t so neat to ^admit defeat.
They can ^see no reasons, 'cause there ^are no reasons,
What ^reasons do you ^need? ^Oh-^oh-^oh^oh.
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus

... The whole day \lrep \[E]down, down, down, shoot it all \[C]down. \rrep
{\nolyrics Zwischenspiel: \[E]\[F]\[G]\[F] \[C]}
\endchorus

\beginverse
And all the ^playing's stopped in the ^playground now, she ^wants to play with the ^toys a while.
And ^school's out early and ^soon we'll be learning and the ^lesson today is ^how to die.
And then the ^bullhorn crackles and the ^captain tackles with the ^problems of the how's and ^why's.
And he can ^see no reasons, 'cause there ^are no reasons.
What ^reason do you need to ^die, ^die? ^Oh-^oh-^oh.
\endverse

\beginchorus
\endchorus

\beginverse
%Siehe Strophe 1.
The ^silicon chip in^side her head gets ^switched to over^load,
and ^nobody’s gonna go to ^school today, he’s gonna ^make them stay at ^home,
and ^daddy doesn’t under^stand it, he always ^said she was good as ^gold,
and he can ^see no reasons, 'cause there ^are no reasons.
What ^reason do you need to be ^show-^ow-^ow-^ow-^own?
\endverse


\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\echo{Tell me \[C]why} I don’t like \[Em]Mondays. \echo{Tell me \[F]why} I don’t like \[G]Mondays.
\lrep\echo{Tell me \[C]why} I don’t like,\[Em] I don’t like,\echo{Tell me \[F]why} I don’t like \[G]Mondays.\rrep
\echo{Tell me \[C]why} I don’t like \[Em]Mondays. I wanna \[F]shoo-oo-woo-woo-woo-\[G]oot
the whole day \[C]down. \[Em]Oh-\[F]oh-\[G]\[F]oh\[C]oh 
\endchorus

\endsong

\beginscripture

\endscripture

\begin{intersong}

\end{intersong}