\beginsong{In The End}[wuw={Linkin Park}, index={It starts with one thing}, jahr=2000, alb={Hybrid Theory}]

\markboth{\songtitle}{\songtitle}

\beginverse
\echo{It starts with...} \[Dm]One thing I don't know why,
it \[C]doesn't even matter how hard you try,
\[B&]keep that in mind I designed this rhyme, to ex\[C]plain in due time... 
\endverse

\beginverse*
\echo{All I \[Dm]know: } Time is a valuable thing,
\[C]watch it fly by as the pendulum swings,
\[B&]watch it count down to the end of the day, the clock \[C]ticks life away.
\endverse

\beginverse*
\echo{It's so un\[Dm]real...} Didn't look out below,
\[C]watch the time go, right out the window,
\[B&]trying to hold on, but didn't even know, or \[C]wasted it all just to...
\endverse

\beginverse*
 \echo{... watch you \[Dm]go!} I kept everything inside, 
and even \[C]though I tried, it all fell apart.
\[B&]What it meant to me will eventually be a memo\[C]ry of a time when...
\endverse

	\beginchorus
	I tried so \[Dm]hard and got so \[F]far, but in the \[C]end it doesn't even \[B&]matter.
	I had to \[Dm]fall to lose it \[F]all, but in the \[C]end it doesn't even \[B&]matter.
	\endchorus

\beginverse
\[Dm]One thing I don't know why,
it \[C]doesn't even matter how hard you try,
\[B&]keep that in mind, I designed this rhyme, to re\[C]mind myself how...
\endverse

\beginverse*
\echo{I tried so \[Dm]hard.} In spite of the way you we're mocking me,
\[C] acting like I was part of your property,
\[B&] remembering all the times you fought with me, \[C]I'm surprised...
\endverse

\beginverse*
 \echo{it got so \[Dm]far.} Things aren't the way they were before,
\[C] you wouldn't even recognize me anymore,
\[B&] not that you knew me back then, but it \[C]all comes back to me...
\endverse

\beginverse*
\echo{in the \[Dm]End...} I kept everything inside, 
and even \[C]though I tried, it all fell apart.
\[B&]What it meant to me will eventually be a memo\[C]ry of a time when...
\endverse

	\beginchorus
	I tried so \[Dm]hard and got so \[F]far, but in the \[C]end it doesn't even \[B&]matter.
	I had to \[Dm]fall to lose it \[F]all, but in the \[C]end it doesn't even \[B&]matter.
	~
	\endchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\lrep I've put my \[Dm]trust in \[C]you, pushed as \[B&]far as I can \[C]go,
and for all \[Dm]this, there's only \[C]one thing you should \[B&]know. \[C] \rrep
~
\endchorus
\renewcommand{\everychorus}{\textnote{\bf Refrain}}

	\printchorus

\endsong
\beginscripture

\endscripture

\begin{intersong}

\end{intersong}