\beginsong{Into The Great Wide Open}[wuw={Tom Petty and the Heartbreakers}, alb={Into The Great Wide Open}, jahr={1991}]

\begin{minipage}{.85\textwidth}%
\interlude{Intro: \[Em Emaj7 Em7 Em6] \rep{2}}

\beginverse\memorize
\[Em] Eddie \[Emaj7]waited 'til he \[Em7]finished highscho\[Em6]ol, 
\[Em] he went to \[Emaj7]Hollywood, \[Em7]got a tatt\[Em6]oo. 
\[Am] He met a \[Am/G]girl out there with \[Am/F#]a tattoo, to\[Am/G]o,
the \[G]future was \[F]wide \[C]open. \[G C G]
\endverse

\beginverse
^ They moved in^to a place, they ^both could affo^rd,
^ he found a ^nightclub, he could ^work at the do^or,
^ she had a ^guitar and she ^taught him some chor^ds,
the ^sky ^was the ^limit. ^ \[G C G D]
\endverse

\end{minipage}%
\begin{minipage}{.15\textwidth}
    \begin{flushright}
    \hfill\gtab{Em}{022000}
    \hfill\gtab{Emaj7}{021000}
    \hfill\gtab{Em7}{020000}
    \hfill\gtab{Em6}{042000}
    \end{flushright}
\end{minipage}%

\beginchorus
\[G]Into the \[Cadd9]great wide \[Dsus4]open, \[G]under them \[Em]skies of \[D]blue, \[Am]
\[G]out in the \[Cadd9]great wide \[Dsus4]open: A \[G]rebel with\[F]out a \[Em]clue. \[A] \[G C G] \[G C G]
\endchorus

\interlude{Solo: \[Em Emaj7 Em7 Em6] \rep{2}}

\beginverse
^ The papers ^said, Ed always ^played from the hea^rt, 
^ he got an ^agent and a ^roadie named Ba^rt.
^ They made a ^record and it ^went in the ^charts, 
the ^sky ^was the ^limit. ^
\endverse

\beginverse
^ His leather ^jacket had ^chains, that would jing^le,
^ they both met ^movie stars, ^partied and mingl^ed.
^ Their A\&^R man said: ''I ^don't hear a sing^le'',
the ^future was ^wide ^open. ^ \[G C G D]
\endverse

\repchorus{2}

\endsong
