\beginsong{Ironic}[wuw={Alanis Morisette}, pfiii={178}, index={An old man}]

\beginverse
An \[F#]old \[H]man \[F#]turned ninety\[G#m]eight, 
he\[F#] won the lotte\[H]ry and \[F#]died the next \[G#m]day.
It's a \[F#]black \[H]fly in \[F#]your chardon\[G#m]nay,
it's a \[F#]death row \[H]pardon two \[F#]minutes too \[G#m]late.
Isn't it \[F#]ironic\[H], don't you \[F#]think? \[G#m]
\endverse

\beginchorus
It's like \[F#]ra-\[H]in on your \[F#]wedding \[G#m]day,
it's a free \[F#]ri\[H]de when you've \[F#]already \[G#m]paid,
it's the good ad\[F#]vi-\[H]ce that you \[F#]just didn't \[G#m]take.
\[A]Who would've \[E]throught, it fi\[F#]gures?
\endchorus

\beginverse
Mr. ^Play-It-^Safe was af^raid to ^fly,
he packed his ^suit^case and kissed his ^kids good-^bye.
He waited his ^whole damn ^life to ^take that ^flight
and as the ^plane crashed ^down he thought: 'Well ^isn't this ^nice?'
And isn't it ^ironic^, don't you ^think? ^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse*
Well \[E]life has a funny way of sneaking up on \[F#]you,
when you think everything's okay and \[E]everything's going right. \[F#] 
And \[E]life has a funny way of helping you \[F#]out,
when you think everything's gone wrong and \[E]everything blows up in your face.\[F#] 
\endverse

\beginverse
A ^traffic ^jam, when you're ^already ^late,
a no-^smoking ^sign on your ^cigarette ^break.
It's like ^ten-thousand ^spoons when all you ^need is a ^knife,
it's ^meeting the man of my ^dreams and then meeting his ^beautiful ^wife.
And isn't it ^ironic^, don't you ^think? ^
A little too \[F#]ironic\[H], and yeah I \[F#]really do \[G#m]think.
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
It's like \[F#]ra-\[H]in on your \[F#]wedding \[G#m]day,
it's a free \[F#]ri-\[H]de when you've \[F#]already \[G#m]paid,
it's the good ad\[F#]vi-\[H]ce that you \[F#]just didn't \[G#m]take.
\[A]Who would've \[E]throught, it fi\[F#]gures?

Well \[E]life has a funny way of sneaking up on \[F#]you.
\[E]Life has a funny, funny way \[F#] of helping you \[E]out,
helping you \[F#]out.
\endchorus

\endsong
