\beginsong{I See Fire}[
    wuw={Ed Sheeran}, 
    alb={"{}The Hobbit"{} Soundtrack}, 
    jahr={2013}, 
    index={Oh, misty eye of the mountain below},
	capo={6},
]


\begin{minipage}{.85\textwidth}%
\beginverse*
Oh, misty eye of the mountain below
Keep careful watch of my brothers' souls
And should the sky be filled with fire and smoke
Keep watching over Durin's \[Em]sons
\nolyrics{\lrep \[Em] \[C] \[D] \[Em] \rrep}
\endverse
\end{minipage}%
\begin{minipage}{.15\textwidth}
	\vspace{0pt}
    \begin{flushright}
    \hfill\gtab{Am7}{X02010}
    \hfill\gtab{G/h}{X20003}
    \end{flushright}
\end{minipage}%


\beginverse
If this is to \[Em]end in \[G]fire, then we should \[D]all burn \[C]together.
Watch the \[Em]flames climb \[G]high \[D]into the \[Am7]night.
Calling \[Em]out fa\[G]ther, oh, \[D]stand by and \[C]we will
watch the \[Am7]flames burn \[G/h]auburn on the \[C]mountain side.
\nolyrics{\[Em] \[C] \[D] \[Em]}
\endverse

\beginverse
And if we should \[Em]die to\[G]night, then we should \[D]all die \[C]together,
raise a \[Em]glass of \[G]wine\[D] for the \[Am7]last time.
Calling \[Em]out fa\[G]ther, oh, \[D]prepare as \[C]we will
watch the \[Am7]flames burn \[G/h]auburn on the \[C]mountain side,
deso\[Am7]lation \[G/h]comes upon the \[C]sky.
\endverse


\beginchorus
Now I see \[Em]fire\[C], \[D]inside the \[Em]mountain, I see \[Em]fire\[C],  \[D]burning the \[Em]trees.
And I see \[Em]fire\[C], \[D]hollowing \[Em]souls, I see \[Em]fire\[C], \[D]blood in the \[Am7]breeze.
And I hope that you'll remember me... 
\nolyrics{\lrep \[Em] \[C] \[D] \[Em] \rrep}
\endchorus

\beginverse
Oh, should my \[Em]people \[G]fall, then surely \[D]I'll do the \[C]same.
Confined in \[Em]mountain \[G]halls, we got too \[D]close to the \[Am7]flame.
Calling \[Em]out fat\[G]her, oh, \[D]hold fast and \[C]we will
watch the \[Am7]flames burn \[G/h]auburn on the \[C]mountain side.
Deso\[Am7]lation \[G/h]comes upon the \[C]sky
\endverse

\beginchorus
Now I see \[Em]fire\[C], \[D]inside the \[Em]mountain, I see \[Em]fire\[C],  \[D]burning the \[Em]trees.
And I see \[Em]fire\[C], \[D]hollowing \[Em]souls, I see \[Em]fire\[C], \[D]blood in the \[Am7]breeze.
And I hope that you'll remember \[Am7]me...
~
And if the \[Am7]night is \[Em]burning I will \[G]cover my \[D]eyes.
For if the \[Am7]dark re\[Em]turns, then my \[G]brothers will \[D]die.
And as the \[Am7]sky is falling \[Em]down it crashed \[G]into this lonely \[D]town.
And with that \[Am7]shadow upon the ground I \[G/h]hear my \[C]people screaming \[D]out:
\endchorus

\beginchorus
Now I see \[Em]fire\[C], \[D]inside the \[Em]mountain, I see \[Em]fire\[C],  \[D]burning the \[Em]trees.
And I see \[Em]fire\[C], \[D]hollowing \[Em]souls, I see \[Em]fire\[C], \[D]blood in the \[Em]breeze.
I see \[Em]fire, oh you \[C]know I saw a city \[D]burning! \echo{\[Em]fire}
I see \[Em]fire, feel \[C]the heat upon my \[D]skin \echo{\[Em]fire}
And I see \[Em]fire,\[C] oooo\[D]oo \echo{\[Em]fire}
And I see \[Em]fire burn \[C]auburn on the \[D]mountain \[Em]side.
\endchorus

\endsong