\beginsong{Jessie}[
    wuw={Joshua Kadison}, 
    alb={Painted Desert Serenade}, 
    jahr={1993}, 
    pfiii={179}, 
    index={From a phone booth in Vegas},
]

\beginverse
{\nolyrics Intro: \[G] \[D/F#] \[Am] \[C]}

\[G]From a phone booth in \[Am]Vegas Jessie \[C]calls at 5 \[G]a.m. 
to \[G]tell me how she's \[Am]tired \[C]of all of \[G]them.
She says:\[G] 'Baby I've been th\[Am]inking about a \[C]trailer by the sea. \[G]
\[G]We could go to \[C]Mexico \[Am]you the cat and \[G]me,
we'll drink \[Em]Tequila\[D] and look for \[C]seashells,
now \[Em]doesn't \[D]that sound \[C]sweet?'
Oh \[Em]Jessie you \[D]always \[C]do this 
\[C]everytime I get back on my \[D]feet. \[C] \[D] \[C] \[D]
\endverse

\beginchorus
\[G]Jessie paint your \[C]pictures about \[G]how it's gonna \[C]be,
by \[G]now I should know \[C]better your \[D]dreams are never free.\[Em] \[D]
But \[G]tell me all \[C]about our little \[G]trailer by the \[C]sea. 
\[G]Jessie you can \[C]always sell \[D]any dream to \[Em]me. \[D]
\[G]Oh Jessie you can \[C]always sell \[D]any dream to \[G]me.
\endchorus

\beginverse
{\nolyrics Bridge: ^ ^ ^ ^ \rep{2}}

^She asks me how the ^cat's been I say: '^Moses he's just ^fine, 
but he ^used to think ^about you ^all the ^time.
We ^finally took your ^pictures ^down off the ^wall.
^Jessie how do you ^always seem to ^know just when to ^call.'
She says: '^Get your ^stuff to^gether,
bring ^Mose and ^drive real ^fast!'
And I ^listen ^to her ^promise,
^I'd swear to God this time it's gonna ^last. ^ ^ ^ ^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse*
I'll \[Em]love you \[D]in the \[C]sunshine,
lay you \[Em]down in the \[D]warm white \[C]sand 
and \[Em]who knows \[D]maybe \[C]this time 
\[C]things will turn out just the way you \[D]planned. \[C] \[D] \[C] \[D]
\endverse

\beginchorus
{\nolyrics Outro: \[G] \[D/F#] \[Am] \[C] \rep{2}}
\endchorus

\endsong
