\beginsong{Kickapoo}[wuw={Tenacious D}, jahr={2006}, alb={The Pick of Destiny}]

\interlude{Intro: \[Dm] \[Am] \[F C-G]}

\renewcommand{\everychorus}{\textnote{\bf Narrator}}
\beginchorus
A \[Dm]long-ass fucking time ago, in a town called Kickapoo,
there \[Am]lived a humble family, religious through and through.
But \[F]yea, there was a black sheep and he \[C]knew just what to \[G]do...
His \[Dm]name was young J.B. and he refused to step in line,
a \[Am]vision he did see-eth, fucking rocking all the time.
He \[F]wrote a tasty jam and all the \[C]planets did a\[G]lign. \[G]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Young JB}}
\beginchorus
Oh, the \[A]dragon's balls were blazin' as I \[C]stepped into his cave,
then I \[G]sliced his fuckin' cockles with a \[A#]long and shiny blade.
'Twas \[A]I who fucked the dragon, fucka\[C]lizing fuckaloo,
and \[G]if you try to fuck with me, then \[A#]I shall fuck you \[A]too!
~\\
\[H-C] Gotta get it \[G]on in the party \[A]zone!
\[H-C] I got to shoot a \[G]load in the party \[A]zone!
\[H-C] Gotta lick a \[G]toad in the party \[A]zone!
\[H-C] Gotta suck a \[G]chode in the party \[A]zone!
\echo{*Hit* - Ahhhh!}
\endchorus


\renewcommand{\everychorus}{\textnote{\bf JBs Father}}
\beginchorus
% \[G-C-G-G ~~~~ B&-D#-B&-B& ~~~~ F-B&-F-F ~~~~ G#-C#-G#-G#]
\[G B& F G#]
You've \[G]disobeyed my orders, son, why \[B&]were you ever born?
Your \[F]brother's ten times better than you, \[G#]Jesus loves him more.
This \[G]music, that you play for us comes \[B&]from the depths of hell.
\[F]Rock and Roll's The Devil's work, he \[G#]wants you to rebel!
You'll be\[G]come a mindless puppet, Beelze\[B&]bub will pull the strings,
your \[F]heart will lose direction and \[G#]chaos it will \[G]bring.
~\\
\[H-C] You'd better shut your \[F]mouth, better watch your \[G]tone.
\[H-C] You're grounded for a \[F]week with no tele\[G]phone.
\[H-C] Don't let me here you \[F]cry, don't let me hear you \[G]moan.
\[H-C] You gotta praise The \[F]Lord when you're in my \[G]home. \[G C G]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Young JB}}
\beginchorus
\[G]Dio can you hear me? I am \[B&]lost and so alone.
I'm \[F]askin' for your guidance, won't you \[G#]come down from your throne?
I \[G]need a tight compadre, who will \[B&]teach me how to rock.
My \[F]father thinks you're evil but man, \[G#]he can suck a cock!
\[G]Rock is not the devil's work, it's \[B&]magical and rad.
I'll \[F]never rock as long as I am \[G#]stuck here with my \[G]dad. \[G# F B& G#]
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Dio}}
\beginchorus
I \[C]hear you, brave young Jables, you are \[C]hungry for the rock,
but to \[C]learn the ancient methods sacred \[B&]doors you must unlock.
Es\[C]cape your father's clutches and this op\[C]pressive neighborhood
On a \[C]journey you must go, to find the \[B&]land of Holly\[C]wood.
~\\
In The \[C]City Of Fallen Angels, where the \[F]ocean meets the \[G#]sand,
you will \[C]form a strong alliance and the \[F]world's most awesome \[G#]band!
To \[C]find your fame and fortune through the \[F]valley you must \[G#]walk,
you will \[C]face your inner demons, now \[F]go, my \[G#]son, and \[G]rock!
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Interlude (2x)}}
\beginchorus
\[G ~ D#--D ~~--~~ G ~ D#--D ~--~ G ~ D#--D ~--~ C ~ D--D# ~ F]
\endchorus


\renewcommand{\everychorus}{\textnote{\bf Narrator}}
\beginchorus
So he \[G]bailed from fuckin' Kickapoo, with hunger in his heart,
and he \[D]journeyed far and wide to find the secrets of his art
But \[B&]in the end he knew, that he would \[F]find his counter\[C]part:
~\\
\[G ~ D#--D ~~--~~ G ~ D#--D ~--~ G ~ D#--D]Rock!
\[C]Rah-\[D]ha-\[D#]ha-\[F]ha-\[G ~ D#--D ~~--~~ G ~ D#--D ~--~ G ~ D#--D]hock!
\[C]Roh-\[D]ho-\[D#]ho-\[F]hey-\[G ~ D#--D ~~--~~ G ~ D#--D ~--~ G ~ D#--D]yayayayaye
\[C ~ D--D# ~ F]yock! ~~~~ \[G]
\endchorus

\endsong