\beginsong{Lady in Black}[
    wuw={Uriah Heep}, 
    alb={Salisbury}, 
    jahr={1971}, 
    pfii={200}, 
    pfiii={104}, 
    kssiv={198}, 
    index={She came to me one morning},
]

\beginverse
She \[Em]came to me one morning, one \[Em]lonely Sunday morning,
her \[D]long hair flowing in the \[Em]mid-winter wind.
I \[Em]know not how she found me, for in \[Em]darkness I was walking,
and \[D]destruction lay around me from a \[Em]fight I could not win.
\endverse

\beginchorus
\[Em]Ahhhhhhh\[D]hhhhhhh, \[Em]ahhh\[D]hhhh\[Em]hh.
\endchorus

\beginverse
She ^asked me name my foe then. I ^said the need within some men
to ^fight and kill their brothers without ^thought of love or God.
And I ^begged her give me horses to ^trample down my enemy,
so ^eager was my passion to ^devour this waste of life.
\endverse

\beginchorus
\[Em]Ahhhhhhh\[D]hhhhhhh, \[Em]ahhh\[D]hhhh\[Em]hh.
\endchorus

\beginverse
But she ^would not think of battle that re^duces men to animals,
so ^easy to begin and yet im^possible to end.
For ^she the mother of all men had ^counciled me so wisely that
I ^feared to walk alone again and ^asked if she would stay.
\endverse

\beginchorus
\[Em]Ahhhhhhh\[D]hhhhhhh, \[Em]ahhh\[D]hhhh\[Em]hh.
\endchorus

\beginverse
'Oh ^lady lend your hand,' I cried, 'Oh ^let me rest here at your side.'
'Have ^faith and trust in me,' she said and ^filled my heart with life.
There ^is no strength in numbers. I've ^no such misconceptions.
But ^when you need me be assured I ^won't be far away.
\endverse

\beginchorus
\[Em]Ahhhhhhh\[D]hhhhhhh, \[Em]ahhh\[D]hhhh\[Em]hh.
\endchorus

\beginverse
Thus ^having spoke she turned away and ^though I found no words to say
I ^stood and watched until I saw her ^black cloak disappear.
My ^labor is no easier, but ^now I know I'm not alone.
I ^find new heart each time I think u^pon that windy day.
And \[Em]if one day she comes to you drink \[Em]deeply from her words so wise.
Take \[D]courage from her as your prize and \[Em]say hello for me.
\endverse

\beginchorus
\lrep \[Em]Ahhhhhhh\[D]hhhhhhh, \[Em]ahhh\[D]hhhh\[Em]hh. \rrep\rep{14}
\endchorus

\endsong
