\beginsong{Lemon Tree}[
    wuw={Fools Garden}, 
    pfiii={157}, 
    kssiv={286}, 
    siru={126}, 
    index={I'm sitting here in a boring room},
]

\beginverse
I’m \[Am]sitting here in a \[Em]boring room, 
it’s \[Am]just another rainy Sunday \[Em]afternoon.
I’m \[Am]wasting my time, I got \[Em]nothing to do, 
I’m \[Am]hanging around, I’m \[Em]waiting for you,
but \[Dm]nothing ever happens. \[Em] And I \[Am]wonder. \[G] \[Am]
\endverse
 
\beginverse
I’m ^driving around ^in my car. 
I’m ^driving too fast, I’m ^driving to far.
I’d ^like to change my ^point of view, 
I ^feel so lonely, I’m ^waiting for you,
but ^nothing ever happens ^ And I ^wonder ^ ^
\endverse

\beginchorus
I \[C]wonder how, I \[G]wonder why.
\[Am]Yesterday you told me 'bout the \[Em]blue blue sky 
and \[F]all that I can \[G]see is just a yellow \[C]lemon tree. \[G] 
I’m \[C]turning my head \[G]Up and down,
I’m \[Am]turning, turning, turning, turning, \[Em]turning around
and \[F]all that I can \[D]see is just another \[G]lemon tree.
\endchorus

\beginverse*
Sing: \[Am]da\[Em], dadadada-\[Am]didada\[Em], dadadada-\[Dm]didada\[Em], dadidi\[Am]da... \[G] \[Am]
\endverse

\beginverse
I’m ^sitting here, I ^miss the power 
I’d ^like to go out ^taking a shower 
But ^there’s a heavy cloud in^side my head 
I ^feel so tired, put my^self into bed 
Well, ^nothing ever happens ^ And I ^wonder ^ ^

\[E]Isolation \[Am]is not good for me 
\[G]Isolation, \[C]I don’t want to\[E] sit on a lemon tree
\endverse

\beginverse
I’m ^stepping around in a ^desert of joy 
^Baby anyhow I’ll get an^other toy 
And \[Dm]everything will happen\[Em] And you'll \[Am]wonder \[G] \[Am]
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
I \[C]wonder how, I \[G]wonder why.
\[Am]Yesterday you told me 'bout the \[Em]blue blue sky 
and \[F]all that I can \[G]see. 
And \[F]all that I can \[G]see.
And \[F]all that I can \[G]see is just the yellow \[C]lemon tree.
\endchorus

\endsong
