\beginsong{Summer of '69}[wuw={Brian Adams}, pfiii={139}, index={I got my first real six-string}]

\markboth{\songtitle}{\songtitle}

\beginverse\memorize
\[D] I got my first real six string,\[A] bought it at the five and dime.
\[D] Played it til my fingers bled,\[A] 'was the summer of '69.
\[D] Me and some guys from school\[A] had a band and we tried real hard.
\[D] Jimmy quit and Jody got married,\[A] I shoulda known we'd never get far.
\endverse

\beginchorus
\[Hm] But when I \[A]look back now,\[D] that summer seemed to \[G]last forever.
\[Hm] And if I \[A]had the choice,\[D] yeah I'd always \[G]wanna be there,
\[Hm] those were the \[A]best days of my \[D]life. \[A]
\endchorus

\beginverse
^ Ain't no use in complainin',^ when you got a job to do.
^ Spent my evenin's down at the drive-in^ and that's when I met you, yeah!
\endverse

\beginchorus 
\[Hm] Standin' on your \[A]mama's porch, \[D]you told me that you'd \[G]wait forever.
\[Hm] Oh and when you \[A]held my hand,\[D] I knew that it was \[G]now or never,
\[Hm] those were the \[A]best days of my \[D]life. Oh \[A]yeah!
Back in the Summer of \[D]'69. \[A]Oh!

\endchorus

\beginverse*
Bridge:
\[F] Man we were \[H&]killin' time we were \[C]young and restless,
we \[H&]needed to unwind. \[F]
I guess \[H&]nothin' can last for\[C]ever - for\[C]ever, no! \[D]\[A]\[D]\[A]
\endverse

\beginverse
^And now the times are changin' ^look at everything that's come and gone.
^Sometimes when I play that old six string ^I think about you'n wonder what went wrong.
\endverse

\beginchorus
\[Hm] Standin' on your \[A]mama's porch, \[D]you told me that you'd \[G]wait forever.
\[Hm] Oh and when you \[A]held my hand,\[D] I knew that it was \[G]now or never,
\[Hm] those were the \[A]best days of my \[D]life. Oh \[A]yeah!
Back in the Summer of \[D]'69. \[A]Oh!
It was the Summer of \[D]'69. \[A]Oh-yeah!
Me and my Baby in \[D]'69. \[A]Oh!
{\nolyrics Outro: \[D]\[A] \rep{4}}
\endchorus



\endsong

\beginscripture

\endscripture

\begin{intersong}
\end{intersong}