\beginsong{Under the Bridge}[wuw={Red Hot Chili Peppers}, pfiii={82}, index={Sometimes I feel}]

\markboth{\songtitle}{\songtitle}

\beginverse*
{\nolyrics Intro: \[D] \[F#] \rep{4}}

\endverse 

\beginverse\memorize
\[E] Sometimes \[H]I feel like I \[C#m]don't have a \[G#]part\[A]ner,
\[E]sometimes \[H]I feel like \[C#m]my only \[A]friend.
Is the \[E]city I \[H]live in, the \[C#m]city of \[G#]an\[A]gels?
\[E]Lonely as \[H]I am, to\[C#m]gether we \[A]cry. \[Emaj7]
\endverse

\beginverse
I ^drive on her ^streets 'cause ^she's my com^pan^ion,
I ^walk through her ^hills 'cause she ^knows who I ^am. 
She ^sees my good ^deeds and she ^kisses me ^win^dy,
^ I never ^worry, now ^that is a ^lie. ^
\endverse

\beginchorus
\[F#m]I don't ever want \[E]to feel\[H] like I \[F#m]did that day,
take me to the place \[E]I love,\[H] take me \[F#m]all the way.
I don't ever want \[E]to feel\[H] like I \[F#m]did that day,
take me to the place \[E]I love,\[H] take me \[F#m]all the way, \[E]ye\[H]ah, \[C#m]yeah, \[A]yeah.
\endchorus

\beginverse
It's ^hard to be^lieve that there's ^nobody ^out ^there,
it's ^hard to be^lieve, that ^I'm all a^lone.
At ^least I have ^love her, the ^city she ^loves ^me,
^lonely as ^I am, to^gether we ^cry.
\endverse

\beginchorus
\[F#m]I don't ever want \[E]to feel\[H] like I \[F#m]did that day,
take me to the place \[E]I love,\[H] take me \[F#m]all the way.
I don't ever want \[E]to feel\[H] like I \[F#m]did that day,
take me to the place \[E]I love,\[H] take me \[F#m]all the way, \[A]ye\[Am7]ah, \[G]yeah, \[Fmaj7]yeah.
\[A]Oh, \[Am7]no, nono, \[G]yeah, \[Fmaj7]yeah.
\[A]Love \[Am7]me, I say: \[G]Yeah, \[Fmaj7]yeah. \[Fmaj7] \[E] \[G] \newline

\echo{\[A]Under the bridge \[Am7]downtown...}\[G] is where I \[Fmaj7]drew some blood.
\echo{\[A]Under the bridge \[Am7]downtown...}\[G] I could not \[Fmaj7]get enough.
\echo{\[A]Under the bridge \[Am7]downtown...}\[G] forgot a\[Fmaj7]bout my love.
\echo{\[A]Under the bridge \[Am7]downtown...}\[G] I gave my \[Fmaj7]life awa\[A]y \[Am7]yeah, \[G]yeah, \[Fmaj7]yeah.
\echo{Away.} \[A]No, \[Am7]no, nono, \[G]yeah, \[Fmaj7]yeah. 
\echo{Away.} \[A]No, \[Am7]no, I say, \[G]yeah, \[Fmaj7]yeah.
\echo{A\[A]w\[Am7]a\[G]y\[Fmaj7].} Here I stay.
{\nolyrics Outro: \[A] \[Am7] \[G] \[Fmaj7] \rep{2} \[A]}
\endchorus


\endsong

\beginscripture

\endscripture

\begin{intersong}
\end{intersong}