\beginsong{Hotel California}[wuw={Eagles}, pfii={196}, pfiii={81}, index={On a dark dessert highway}]	

\markboth{\songtitle}{\songtitle}

\beginverse

\[Hm]On a dark desert highway, \[F#]cool wind in my hair.
\[A]Warm smell of colitas \[E]rising up through the air.
\[G]Up ahead in the distance, \[D]I saw a shimmering light.
\[Em]My head grew heavy and my sight grew dim, \[F#]I had to stop for the night.

\[Hm]There she stood in the doorway,  \[F#]I heard the mission bell.
\[A]And I was thinking to myself this could be \[E]heaven or this could be hell.
\[G]Then she lit up a candle, \[D]and she showed me the way.
\[Em]There were voices down the corridor,\[F#] I thought I heard them say:
\endverse

\beginchorus
\[G]Welcome to the Hotel Cali\[D]fornia.
Such a \[F#m]lovely place, such a \[Hm7]lovely face.
\[G]Plenty of room at the Hotel Cali\[D]fornia.
\[Em]Any time of year \echo{any time of year} you can \[F#]find it here.
\endchorus 

\beginverse
^Her mind is Tiffany-twisted, ^she got the Mercedes Benz. 
^She got a lot of pretty, pretty boys, ^that she calls friends. 
^How they dance in the courtyard, ^sweet summer sweat. 
^Some dance to remember, ^some dance to forget.

^So I called up the Captain, ^'Please bring me my wine'.
He said, ^'We haven't had that spirit here since ^nineteen sixty nine'.
^And still those voices are calling from ^far away, 
^wake you up in the middle of the night, ^just to hear them say:
\endverse

\beginchorus
\[G]Welcome to the Hotel Cali\[D]fornia.
Such a \[F#m]lovely place \echo{such a lovely place}, such a \[Hm7]lovely face.
they're \[G]living it up at the Hotel Cali\[D]fornia. 
what a \[Em]nice surprise \echo{what a nice surprise} bring your \[F#]alibis.
\endchorus

\beginverse
^Mirrors on the ceiling, ^the pink champagne on ice. 
And she said ^'We are all just prisoners here, ^of our own device'.
^And in the master's chambers, they ^gathered for the feast. 
^They stab it with their steely knives, but they ^just can't kill the beast.

^Last thing I remember, ^I was running for the door. 
^I had to find the passage back to the ^place I was before.
^'Relax,' said the night man, 'we are ^programmed to receive.
^You can check out any time you like, but ^you can never leave!'
\endverse

\beginchorus
\[G]Welcome to the Hotel Cali\[D]fornia.
Such a \[F#m]lovely place, such a \[Hm7]lovely face.
\[G]Plenty of room at the Hotel Cali\[D]fornia.
\[Em]Any time of year (any time of year) you can \[F#]find it here. \rep{2}
\endchorus
\endsong

\begin{intersong}
\end{intersong}