\beginsong{What shall we do with the drunken sailor}[wuw={nach einem Arbeitslied der Seefahrer}, pfii={209}, pfiii={111}]

\markboth{\songtitle}{\songtitle}

\beginverse
\[Dm]What shall we do with the drunken sailor? \[C]What shall we do with the drunken sailor?
\[Dm]What shall we do with the drunken sailor? \[C]Earl-aye in the \[Dm]morning?
\endverse

\beginchorus
\[Dm]Hoo-ray, and up she rises, \[C]Hoo-ray, and up she rises
\[Dm]Hoo-ray, and up she rises, \[C]Earl-aye in the \[Dm]morning?
\endchorus

\beginverse
^Put him in the long boat till he's sober. ^Put him in the long boat till he's sober.
^Put him in the long boat till he's sober. ^Earl-aye in the ^morning
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse
^Put him in the scuppers with a hose-pipe on him. ^Put him in the scuppers with a hose-pipe on him. 
^Put him in the scuppers with a hose-pipe on him.  ^Earl-aye in the ^morning.
\endverse

\beginchorus
\endchorus

\beginverse
^Shave his belly with a rusty razor. ^Shave his belly with a rusty razor.
^Shave his belly with a rusty razor. ^Earl-aye in the ^morning.
\endverse

\beginchorus
\endchorus


\beginverse
^Put him in bed with the captain's daughter. ^Put him in bed with the captain's daughter.
^Put him in bed with the captain's daughter. ^Earl-aye in the ^morning.
\endverse

\beginchorus
\endchorus


\beginverse
^Take him and shake him and try to awake him. ^Take him and shake him and try to awake him.
^Take him and shake him and try to awake him. ^Earl-aye in the ^morning.
\endverse

\beginchorus
\endchorus


\endsong

\beginscripture{}

\endscripture

\begin{intersong}

\end{intersong}