\beginsong{Blowing in the Wind}[wuw={Bob Dylan}, pfii={225}, pfiii={117}, index={How many roads must a man walk down}]

\markboth{\songtitle}{\songtitle}

\beginverse
\[D]How many \[G]roads must a \[D]man walk down,
before you can \[G]call him a \[D]man? \[A7]
Yes, n \[D]how many \[G]years must a \[D]white dove sail, 
before she \[G]sleeps in the \[A7]sand?
Yes, n \[D]how many \[G]times must the \[D]cannonballs fly,
before they for\[G]ever are \[D]banned? \[A7]
\endverse

\beginchorus
The \[G]answer my \[A7]friend, is \[D]blowing in the \[Hm]wind,
the \[G]answer is \[A7]blowing in the \[D]wind.
\endchorus

\beginverse
^How many ^times must a ^man look up,
before he can ^see the ^sky? ^
Yes, n ^how many ^ears must ^one man have,
before he can ^hear people ^cry?
Yes, n ^how many ^deaths will it ^take 'till he knows,
that too many ^people have ^died? ^
\endverse

\beginchorus
The \[G]answer my \[A7]friend, is \[D]blowing in the \[Hm]wind,
the \[G]answer is \[A7]blowing in the \[D]wind.
\endchorus

\beginverse
^How many ^years can a ^mountain exist,
before it is ^washed to the ^sea? ^
Yes, n ^how many ^years can some ^people exist,
before they're al^lowed to be ^free?
Yes, n ^how many ^times can a ^man turn his head,
pretending he ^just doesn't ^see? ^
\endverse

\beginchorus
The \[G]answer my \[A7]friend, is \[D]blowing in the \[Hm]wind,
the \[G]answer is \[A7]blowing in the \[D]wind.
\endchorus


\endsong

\beginscripture

\endscripture

\begin{intersong}
\end{intersong}