\beginsong{Lonely}[
    wuw={In Legend}, 
    alb={Stones at Goliath}, 
    jahr={2015},
]

\beginverse
\[B&m]I kept your picture in\[C#]side a map,
I let it \[G#]frame by all our \[F#]places.
\[B&m] Though you and me never \[C#]made it back
they were the \[G#]shelters of my \[F#]mind.
\endverse

\beginverse
I ^wonder how did the ^simple things
ever ^got so compli^cated?
^ Why you and me followed ^gravity 
with any ^parachutes de^clined.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
'Cause we were \[E&]lonely, lonely, \[F#]lonely, lonely,
I'm \[C#]lonely, lonely, \[G#]lonely, lonely.
\[E&]Lonely, lonely, \[F#]lonely, lonely,
I'm \[C#]lonely, lonely, \[G#]aaahhh.
\endchorus

\beginverse
^ But now the places did ^change a lot 
and with them ^all our former ^traces.
^ Your picture’s still a good-^looking shot,
though all your ^colours fade a^way.
~\\
\[E&m]I started \[B&m]painting again, a \[G#]little rusty though
\[E&m]You used to \[B&m]tell me then, \[F#]not to let \[G#]go...
\endverse

\renewcommand{\everychorus}{\textnote{\bf Pre-Chorus}}
\beginchorus
Choose the \[F#]changing, choose re\[B&m]bellion,
choose the \[G#]things worth living for.
I’m glad we’re \[F#]talking, I’m glad we’re \[B&m]dreaming,
but let \[G#]action follow thoughts...
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Chorus (2x)}}
\beginchorus\endchorus
\renewcommand{\everychorus}{\textnote{\bf Pre-Chorus}}
\beginchorus\endchorus
\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus\endchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
(I) hold you \[F#]dear to my \[C#]heart, no \[B&m]matter what we \[G#]went through.
Because you’re \[F#]always a \[C#]part of \[B&m]our different \[G#]story.
No matter \[F#]where you’re right \[C#]now, I \[B&m]know you’re doing \[G#]fine,
‘cause the \[F#]more we do \[C#]change, the \[B&m]more we \[F#]stay the \[G#]same.
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Pre-Chorus (2x)}}
\beginchorus\endchorus
\renewcommand{\everychorus}{\textnote{\bf Chorus (2x)}}
\beginchorus\endchorus

\endsong

