\beginsong{Lord of the Dance}[wuw={Sydney Carter}, pfii={208}, pfiii={110}, gruen={296}, index={I danced in the morning}]

\beginchorus
\[D]Dance, dance, wherever you may be.
I am the lord of the \[A]dance, said he.
And I \[D]lead you all wherever you may be,
and I \[A]lead you all in the \[D]dance \[A]said \[D]he.
\endchorus

\beginverse
I \[D]danced in the morning when the world was young.
I \[Em]danced in the moon and the \[G]stars and the \[A]sun.
I \[D]came down from Heaven and I danced on the Earth.
At \[Em]Bethlehem I \[D]had \[A]my \[D]birth.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse
I ^danced for the Scribe and the Pharisees.
They ^would not dance and they ^wouldn't follow ^me.
I ^danced for the fishermen James and John.
They ^came with me so the ^dance ^went ^on.
\endverse

\beginchorus
\endchorus

\beginverse
I ^danced on the Sabbath and I cured the lame,
the ^holy people ^said it was a ^shame.
They ^ripped me and they stripped me and they hung me high,
^left me there on the ^cross ^to ^die.
\endverse

\beginchorus
\endchorus

\beginverse
I ^danced on a Friday when the world turned black,
it's ^hard to dance with the ^devil on your ^back.
They ^buried my body, they thought I was gone,
but ^I am the dance, and the ^dance ^goes ^on.
\endverse

\beginchorus
\endchorus

\beginverse
They ^cut me down and I leap up high, 
I ^am the life that will ^never never ^die.
I'll ^live in you if you'll live in me.
^I am the Lord of the ^dance, ^said ^he.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (x2)}}
\beginchorus
\endchorus

\endsong
