\beginsong{Man on the moon}[wuw={R.E.M.}, alb={Automatic for the People}, jahr={1992}, pfiii={161}, index={Mott the Hoople}]

\beginverse
\[C]Mott the Hoople and the \[Dadd4]Game of Life. \[C]Yeah, yeah, yeah, yeah
\[C]Andy Kaufman in the \[Dadd4]wrestling match. \[C]Yeah, yeah, yeah, yeah
\[C]Monopoly, twenty one, \[Dadd4]checkers, and chess. \[C]Yeah, yeah, yeah, yeah
\[C]Mister Fred Blassie in a \[Dadd4]breakfast mess. \[C]Yeah, yeah, yeah, yeah
\[C]Let's play Twister, \[Dadd4]let's play Risk. \[C]Yeah, yeah, yeah, yeah
\[C]See you in heaven if you \[Dadd4]make the list. \[C]Yeah, yeah, yeah, yeah
\endverse

\beginchorus
Hey \[Am]Andy, did you hear about \[G]this one? \[Am]Tell me, are you locked in the \[G]punch?
Hey \[Am]Andy, are you goofing on \[G]Elvis? Hey \[C]baby\[D], are we losing touch?
\[G]If you be\[Am]lieve\[C] they put a \[Hm]man on the \[G]moon, \[Am]man on the \[D]moon.
\[G]If you be\[Am]lieve\[C] there's nothing \[Hm]up my \[Am]sleeve, then nothing is cool.
\endchorus

\beginverse
^Moses went walking with the ^staff of wood. ^Yeah, yeah, yeah, yeah
^Newton got beaned by the ^apple good. ^Yeah, yeah, yeah, yeah
^Egypt was troubled by the ^horrible asp. ^Yeah, yeah, yeah, yeah
^Mister Charles Darwin had the ^gall to ask. ^Yeah, yeah, yeah, yeah
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}

\beginchorus
\endchorus

\beginverse
^Here's a little agit for the ^never-believer. ^Yeah, yeah, yeah, yeah
^Here's a little ghost for the ^offering. ^Yeah, yeah, yeah, yeah \newpage
^Here's a truck stop in^stead of Saint Peter's. ^Yeah, yeah, yeah, yeah
^Mister Andy Kaufman's gone ^wrestling. ^Yeah, yeah, yeah, yeah
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
Hey \[Am]Andy, did you hear about \[G]this one? \[Am]Tell me, are you locked in the \[G]punch?
Hey \[Am]Andy, are you goofing on \[G]Elvis? Hey \[C]baby\[D], are we losing touch?
\lrep \[G]If you be\[Am]lieve\[C] they put a \[Hm]man on the \[G]moon, \[Am]man on the \[D]moon.
\[G]If you be\[Am]lieve\[C] there's nothing \[Hm]up my \[Am]sleeve, then nothing is cool. \rrep \rep{3} \[Em]
\endchorus

\endsong
