\beginsong{Mrs. Robinson}[wuw={Simon And Garfunkel}, pfii={226}, pfiii={118}, index={And here's to you}]

\beginverse
We'd \[E7]like to know a little bit about you for our files,
we'd \[A7]like to help you learn to help yourself.
\[D7] Look around you \[G]all you see are \[C]sympathetic \[Am]eyes,
\[E] stroll around the grounds un\[D7]til you feel at home.
\endverse

\beginchorus
And here's to \[G]you Mrs. \[Em]Robinson,
\[G]Jesus loves you \[Em]more than you will \[C]know, oh oh \[D7]oh.
God bless you \[G]please Mrs. \[Em]Robinson.
\[G]heaven holds a \[Em]place for those who \[C]pray, hey hey \[Am]hey, hey hey \[E]hey.
\endchorus

\beginverse
^ Hide it in a hiding place where no one ever goes,
^ put it in your pantry with your cupcakes.
^ It's a little ^secret just the ^Robinsons' af^fair,
^ most of all you've got to ^hide it from the kids.
\endverse

\beginchorus
Coo-coo, ca-\[G]choo Mrs. \[Em]Robinson,
\[G]Jesus loves you \[Em]more than you will \[C]know, oh oh \[D7]oh.
God bless you \[G]please Mrs. \[Em]Robinson.
\[G]heaven holds a \[Em]place for those who \[C]pray, hey hey \[Am]hey, hey hey \[E]hey.
\endchorus

\beginverse
^ Sitting on a sofa on a Sunday afternoon,
^ going to the candidates debate, yeah.
^ Laugh about it, ^shout about it ^when you've got to ^choose
^ every way you look at it you ^lose.
\endverse

\beginchorus
Where have you \[G]gone Joe Di \[Em]Maggio?
A \[G]nation turns its \[Em]lonely eyes to \[C]you, ooh ooh \[D7]ooh.
What's that you \[G]say Mrs. \[Em]Robinson?
\[G]Joltin's Joe has \[Em]left and gone a\[C]way, hey hey \[Am]hey, hey hey \[E]hey.
\endchorus


\endsong
