\beginsong{My Friends}[
    wuw={Red Hot Chili Peppers}, 
	alb={One Hot Minute},
	jahr={1995},
]

\begin{minipage}{.9\textwidth}%
\beginverse*
\nolyrics Intro:
\[Dsus2] \[Dsus2/F] \[G] \[Cadd9] \[Dsus2] \[Dsus2/F] \[G] \[F6/9]
\endverse

\beginverse\memorize
\[Dsus2]My friends are \[Dsus2/F]so depressed, \[G]
I \[Cadd9]feel the \[Dsus2]question of your \[Dsus2/F]loneliness. \[G]
Confide,\[F6/9] 'cause \[Dsus2]I'll be on your \[Dsus2/F]side \[G]
You \[Cadd9]know I will,\[Dsus2] You \[Dsus2/F]know I \[G]will. \[Cadd9]
\endverse

\beginverse
^Ex-girlfriend ^called me up, ^
a^lone and ^desperate on the ^prison phone. ^
They ^want to ^give her seven ^years, ^
for ^being sad.
\endverse

\end{minipage}%
\begin{minipage}{.1\textwidth}%
\gtab{Dsus2}{XX0230}
\gtab{Dsus2/F}{100230}
\gtab{Cadd9}{X32033}
\gtab{F6/9}{100013}
\end{minipage}%



\beginchorus
\[C]I love \[Asus2]all of you,
\[C] hurt \[D]by the \[Aadd2]cold.
\[C] So hard and \[Asus2]lonely too,
\[C] when \[D]you don't \[Aadd2]know yourself
\endchorus

\beginverse
^My friends are ^so distressed ^
and ^standing ^on the brink of ^emptiness. ^
No words^ I ^know of to ^express ^
This ^emptiness
\endverse

\beginchorus
\[C]I love \[Asus2]all of you,
\[C] hurt \[D]by the \[Aadd2]cold.
\[C] So hard and \[Asus2]lonely too,
\[C] when \[D]you don't \[Aadd2]know yourself
\endchorus

\beginverse*
{\nolyrics \[Dsus2] \[Dsus2/F] \[G/H] \[Cadd9] \[Dsus2] \[Dsus2/F] \[Cadd9] \rep{2}}

\[F6/9] \[E]Imagine \[G]me, \[F#7]Taught by trage\[F]dy
Re\[C]lease is \[Hsus]peace. \[F] \[F7]
\endverse

\beginverse
^I heard a ^little girl, ^
and ^what she ^said was something ^beautiful. ^
To ^give your ^love no matter ^what. ^
Is ^what she said.
\endverse


\beginchorus
\[C]I love \[Asus2]all of you,
\[C] hurt \[D]by the \[Aadd2]cold.
\[C] So hard and \[Asus2]lonely too,
\[C] when \[D]you don't \[Aadd2]know yourself.
\endchorus

\beginverse*
{\nolyrics \[Dsus2] \[Dsus2/F] \[G/H] \[Cadd9] \[Dsus2] \[Dsus2/F] \[Cadd9] \rep{3}}
\endverse

\endsong
