\beginsong{Narcotic}[
    wuw={Liquido}, 
    alb={Liquido}, 
    jahr={1999}, 
    pfiii={164}, 
    index={So you face it with a smile},
]

\beginverse
\[D] So you face it with a \[Em]smile, 
there is no need to \[G]cry for a trifle's more than \[D]this. \[A]
\[D] Will you still recall my \[Em]name 
and the month it all be\[G]gan, will you release me with a \[D]kiss? \[A]
\[D] Have I tried to draw the \[Em]veil. 
If I have, how could I \[G]fail? Did I fear the conse\[D]quence? \[A]
\[D] Dazed by careless \[Em]words, cosy in my {\[A#]\[C]\[D]mind.}
\endverse

\beginchorus
I don't \[Em]mind I think \[G]so I will \[D]let you go \[A#]\[C] \rep{2}
\endchorus

\beginverse
^ Now you shaped that liquid wax, ^
fit it out with crater cracks^, sweet devotion my de^light. ^
^ Oh, you're such a pretty ^one 
and the naked thrills of ^flesh and skin would tease me through the ^night. ^
^'Now I hate to leave you ^bare,
if you need me I'll be ^there, don't you ever let me ^down.' ^
^ Dazed by careless ^words, cosy in my {^^^mind.}
\endverse

\printchorus

\beginverse
And I touched your \[Em]face,
narcotic mind from \[G]lazed, Mary-\[D]Jane.
And I called your \[Em]name, 
like an addicted to co\[G]caine calls for the stuff he'd rather \[D]blame.
And I touched your \[Em]face, 
narcotic mind from \[G]lazed, Mary-\[D]Jane.
And I called your \[Em]name, my co\[G]caine! \[D]
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
I don't \[Em]mind I think \[G]so I will \[D]let you go \[A]\[D] \rep{5}
\endchorus


\endsong
