\beginsong{Otherside}[
    wuw={Red Hot Chili Peppers}, 
    alb={Californication}, 
    jahr={1999}, 
    index={How long will I slide},
]

\beginchorus
\[Am] How long, how \[F]long will I \[C]slide, \[G]seperate my \[Am]si\[F]de. I \[C]don’t,
I \[G]don’t believe it’s \[Am]b\[F]ad, \[C]slit my throat it’s \[G]all I ever. 
\endchorus

\beginverse
\[Am]I heard your voice through a \[Em]photograph,
\[Am]I thought it up it brought \[Em]up the past,
\[Am]Once you know you can \[Em]never go back, 
I’ve got to \[G]take it on the \[Am]otherside.
\endverse

\beginverse
^Centuries are what it ^meant to me,
^ A cemetery where I ^marry the sea, 
^stranger things could never ^change my mind,
I’ve got to ^take it on the ^otherside.
\[G]Take it on the \[Am]otherside. \[G]Take it on, \[Am]take it on.
\endverse

\printchorus

\beginverse
^Poor my life into a ^paper cup,
^ The ashtray’s full and I’m ^spilling my guts,
^ She wants to know am I ^still a slut. 
I’ve got to ^take it on the ^otherside.
\endverse

\beginverse
^Scarlet starlet and she's ^in my bed,
^ a candidate for my ^soul mate bled,
^ push the trigger and ^pull the thread.
I’ve got to ^take it on the ^otherside.
\[G]Take it on the \[Am]otherside. \[G]Take it on, \[Am]take it on.
\endverse

\printchorus

\beginverse*
{\nolyrics Zwischenspiel: \[Em]\[C]\[Em]\[C]}
\[Em]Turn me on take me for a hard ride,
\[C]burn me out leave me on the otherside,
\[Em] I fell and tell it that it’s not my friend,
I tear it \[C]down I tear it down and it’s born again.
{\nolyrics Bridge: \[Am]\[F]\[C]\[G]}
\endverse

\beginchorus
\[Am] How long, how \[F]long will I \[C]slide, \[G]seperate my \[Am]si\[F]de. I \[C]don’t,
I \[G]don’t believe it’s \[Am]b\[F]ad, \[C]slit my throat it’s \[G]all I ever. \[Am]
\endchorus

\endsong
