\beginsong{Over My Shoulder}[
    wuw={Mike \& The Mechanics}, 
    alb={Beggar On a Beach of Gold}, 
    jahr={1995},
]

\beginchorus
Looking \[Em7]back, \[A]over my \[D]shoulder,
\[Em7] I can see that \[A]look in your \[D]eyes,
\[Em7] I never dreamed, \[A]it could be \[D]over, 
\[Em7]I never wanted\[A] to say good\[D]bye.
Looking \[Em7]back, \[A]over my \[D]shoulder,
\[Em7] with an aching \[A]deep in my \[D]heart,
\[Em7] I wish we \[A]were starting \[D]over, 
\[Em7]oh instead of drifting\[A] so far a\[D]part.
\endchorus

\beginverse\memorize
\[C] Every\[G]body \[F]told me you were \[G]leaving,
\[C] funny \[G]I should \[F]be the last to \[G]know.
\[C] Baby \[G]please, \[F]tell me that I'm \[G]dreaming, 
\[Am]I just never want to let you \[B&]go.
\endverse

\beginchorus
Looking \[Em7]back, \[A]over my \[D]shoulder,\[Em7] I can see that \[A]look in your \[D]eyes,
\[Em7]Turning my heart \[A]over and \[D]over, \[Em7]I never wanted\[A] to say good\[D]bye.
\endchorus

\beginverse
^ I don't ^mind ^everybody ^laughing,
^ but it's e^nough to ^make a grown man ^cry,
^ 'cause I can ^feel you ^slipping through my ^fingers, 
^I don't even know the reason ^why.
\endverse

\beginchorus
\[Em7] \[A] \[D] \[Em7] \[A] \[D]
\[Em7] \[A] \[D] \[Em7] \[A] \[D]
\endchorus

\beginverse
^Every ^day ^it's a losing ^battle,
^ just to ^smile and ^hold my head up ^high.
^ could it ^be, that ^we belong to^gether, 
^Baby won't you give me one more ^try? \[C D E]
\[F]One more \[G]try?
\endverse

\beginchorus
Looking \[Em7]back \[A]over my \[D]shoulder,\[Em7] I can see that \[A]look in your \[D]eyes,
\[Em7] I never dreamed \[A]it could be \[D]over, \[Em7]I never wanted\[A] to say good\[D]bye.
Looking \[Em7]back \[A]over my \[D]shoulder,\[Em7] oh with an aching \[A]feeling in\[D]side,
\[Em7] cutting me up, \[A]deeper and \[D]deeper, \[Em7]fills me with a sadness\[A] that I can't \[D]hide.
Looking \[Em7]back \[A]over my \[D]shoulder,\[Em7] I can see that \[A]look in your \[D]eyes,
\[Em7]{ I never} dreamed, no no, \[A]it could be \[D]over, \[Em7]{I never} wanted\[A] to say good\[D]bye.
\endchorus

\endsong
