\beginsong{Price Tag}[
    wuw={Jessie J}, 
    alb={Who You Are}, 
    jahr={2011}, 
    index={Seems like everybody's got a price}, 
]

\beginverse*
\[F] \echo{O\[Am]kay, Coconut man, \[Dm]Moonheads and Pea.\[B&] You ready?}
\endverse

\beginverse\memorize
\[F] Seems like everybody's got a \[Am]price, I wonder how they sleep at \[Dm]night
When the sale comes first and the \[B&]truth comes second
just stop for a minute and \[F]smile.
Why is everybody so \[Am]serious? Acting so damn mys\[Dm]terious.
Got shades on your eyes, and your \[B&]heels so high that you 
can't even have a good \[F]time.
Everybody look to their \[Am]left, everybody look to their \[Dm]right.
Can you feel that, yeah, we're \[B&]paying with love tonight.
\endverse

\beginchorus
It's not about the \[F]money, money, money, we don't need your \[Am]money, money, money.
We just wanna make the \[Dm]world dance, forget about the \[B&]price tag.
Ain't about the, \[F]uh, cha-ching cha-ching, Ain't about the, \[Am]yeah, b-bling b-bling.
Wanna make the \[Dm]world dance, forget about the \[B&]price tag.
\endchorus

\beginverse
\[F] We need to take it back in \[Am]time, when music made us all u\[Dm]nite
And it wasn't low blows and \[B&]video hoes, am I the only the one getting\[F] tired?
Why is everybody \[Am]so obsessed? Money can't buy us \[Dm]happiness
Can we all slow down and en\[B&]joy right now? Guarantee we'll be feeling \[F]alright.
Everybody look to their \[Am]left, everybody look to their \[Dm]right.
Can you feel, yeah, we're \[B&]paying with love tonight.
\endverse

\printchorus

\beginchorus
\lrep \[F]La, la lala la-la-la, ey. \[Am]La, la lala la-la-la, ey.
\[Dm]La, la lala la-la-la, ey. \[B&]Price tag! \rrep
It's not about the \[F]money, money, money, we don't need your \[Am]money, money, money.
We just wanna make the \[Dm]world dance, forget about the \[B&]price tag.
Ain't about the, \[F]uh, cha-ching cha-ching, Ain't about the, \[Am]yeah, b-bling b-bling.
Wanna make the \[Dm]world dance, forget about the \[B&]price tag.
\[F]Ahh, ahh, ahh, ahh, yeah yeah.
\[Am]Ooh, ooh, ooh.
Forget about the \[Dm]price tag
\[B&]Ahh, ahh.
\endchorus

\endsong
