\beginsong{Riptide}[
    wuw={Vance Joy}, 
    alb={Dream Your Life Away}, 
    jahr={2014}, 
    index={I was scared of dentists and the dark},
]

\beginverse\memorize
\[Am]I was scared of \[G]dentists and the \[C]dark,
\[Am]I was scared of \[G]pretty girls and \[C]starting conversations.
Oh, \[Am]all my friends\[G] are turning \[C]green,
you're the \[Am]magician's as\[G]sistant in their \[C]dream.
\[Am]O\[G]h\[C]h. \[Am]Oh\[G] and they \[C]come unstuck:
\endverse

\beginchorus
\[Am]Lady, \[G]running down to the \[C]riptide, taken away to the \[Am]dark side,
\[G]I wanna be your \[C]left hand man.
I \[Am]love you \[G]when you're singing that \[C]song and I got a lump in my \[Am]throat 'cause
\[G]you're gonna sing the words\[C] wrong.
\endchorus

\beginverse
^Is this movie ^that I think you'll ^like,
this ^guy decides to ^quit his job and ^heads to New York City.
This ^cowboy's ^running from him^self,
and ^she's been living ^on the highest ^shelf.
^O^h^h. ^Oh^ and they ^come unstuck:
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[]
\[Am]I just wanna, I just wanna \[G]know,
\[C]if you're gonna, if you're gonna \[Fmaj7]stay.
\[Am]I just gotta, I just gotta \[G]know,
\[C]I can't have it, I can't have it \[Fmaj7]any other way.
\endchorus

\beginverse
I ^swear she's ^destined for the ^screen,
^closest thing to ^Michelle Pfeiffer ^that you've ever seen, oh:
\endverse

\repchorus{2}

\beginchorus
\[Am]Lady, \[G]running down to the \[C]riptide, taken away to the \[Am]dark side,
\[G]I wanna be your \[C]left hand man.
I \[Am]love you \[G]when you're singing that \[C]song and 
\lrep I got a lump in my \[Am]throat because 
\[G]you're gonna sing the \[C]words wrong. \rrep
\endchorus

\endsong
