\beginsong{Rolling In The Deep}[wuw={Adele, Paul Epworth}, alb={21}, jahr=2010]

\beginverse
\[Am]There's a fire start\[Em]ing in my heart,
Rea\[G]ching a fever pitch, and it's bring\[Em]ing me out the dark. \[G]
\[Am]Finally, I can see \[Em]you crystal clear.
Go \[G]ahead and sell me out, and I'll \[Em]lay your ship \[G]bare. 
\endverse

\beginverse
^See how I'll leave with eve^ry piece of you,
don't un^derestimate the ^things that I will do. ^
^There's a fire start^ing in my heart,
reach^ing a fever pitch, and it's bring^ing me out the dark. ^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[F] The scars of \[G]your love, remind me \[Em]of us,
they keep me \[F]thinking that we almost \[G]had it \[F]all.
The scars of \[G]your love, they leave me \[Em]breathless,
I can't help \[E7]feeling...
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
We could have had it \[Am]a\[G]ll, \hfill\echo{\[Am]You're gonna wish you, \[G]never had met me,}
Rolling in the \[F]Deep. \hfill\echo{\[F]tears are gonna fall, rolling in the \[G]deep.}
You \[G]had my heart in\[Am]side of your \[G]hand, \hfill\echo{\[Am]You're gonna wish you, \[G]never had met me,}
and you \[F]played it to the \[F]beat. \[G] \hfill\echo{\[F]tears are gonna fall, \[F]rolling in the \[G]deep.}
\endchorus

\beginverse
^Baby I have no sto^ry to be told,
But I've ^heard one on you. Now I'm gonna ^make your head burn ^
^Think of me in the depths ^of your despair,
make ^a home down there, as mine ^sure won't be shared. ^
\endverse

\renewcommand{\everychorus}{\textnote{\bf Bridge and Refrain}}
\beginchorus\endchorus

\renewcommand{\everychorus}{\textnote{\bf Refrain (alt.)}}
\beginchorus
Could have had it \[F]a\[G]ll, Rolling in the \[Am]De\[G]ep.
You had my heart in\[F]side of your hand, but you pl\[G]ayed it with a be\[G]ating.
\endchorus

\beginverse
Throw yourself through every open door, \hfill\echo{Whoa}
count your blessings to find what you look for. \hfill\echo{Whoa-uh}
Turn my sorrow into treasured gold, \hfill\echo{whoa}
you'll pay me back in kind and reap just what you sow.
\endverse

\repchorus{3}

\endsong












