\beginsong{Rose Tattoo}[
	txt={Dropkick Murphys},
	alb={Signed and Sealed in Blood},
	jahr={2013},
]

\beginverse*
\nolyrics Intro: \[Am] \[C] \[G] \[Am] \rep{2}
\endverse

\beginverse\memorize
The \[Am]pictures tell the story, this \[C]life has many shades.
I'd \[G]wake up every morning and be\[Am]fore I'd start each day,
I'd take a \[Am]drag from last night's cigarette, that \[C]smoldered in its tray,
\[G]down a little something and \[Dm]then be on my way. \[Am]
\endverse

\beginverse
I ^traveled far and wide and laid this ^head in many ports,
I was ^guided by a compass, I saw ^beauty to the north.
I drew the ^tales of many lives and wore the ^faces of my own,
I had these ^memories all around me so I ^wouldn't be alone.
\endverse

\beginchorus
\[C]Some may be from showing up, \[G]others are from growing up,
\[Dm]sometimes I was so messed up and \[Am]didn't have a clue.
I ain't \[C]winning no one over, I \[G]wear it just for you,
I got your \[Dm]name written here in a rose tattoo.
In a \[Am]rose tattoo, in a \[C]rose tattoo
I got your \[Dm]name written here in a rose \[G]tat\[Am]too. \[Am] \[C] \[G] \[Am]
\endchorus

\beginverse
^This one's for the mighty sea, ^mischief, gold and piracy
^This one's for the man that raised me, ^taught me sacrifice and bravery
^This one's for our favorite game, ^black and gold, we wave the flag
^This one's for my family name, with ^pride I'll wear it to the grave
\endverse

\printchorus

\beginchorus
% \[C]Some may be from showing up, \[G]others are from growing up,
% \[Dm]sometimes I was so messed up and \[Am]didn't have a clue.
% I ain't \[C]winning no one over, I \[G]wear it just for you,
% I got your \[Dm]name written here in a rose tattoo.
In a \[Am]rose tattoo, in a \[C]rose tattoo
I got your \[Dm]name written here in a rose \[G]tat\[Am]too.
\endchorus

\beginverse*
\[F]This one means the most to me, it \[C]stays here for eternity,
a \[G]ship that always stays the course, an \[Am]anchor for my every choice.
A \[F]rose that shines down from above, I \[C]signed and sealed these words in blood,
I \[G]heard them once, sung in a song, it \[G]played again and we sang along.
\endverse

\beginverse
{\nolyrics ^ ^ - ^ ^}
You’ll ^always be here with me, ^even if you’re gone
You’ll ^always have my love, our ^memory will live on
\endverse

\printchorus

\beginchorus
% \[C]Some may be from showing up, \[G]others are from growing up,
% \[Dm]sometimes I was so messed up and \[Am]didn't have a clue.
% I ain't \[C]winning no one over, I \[G]wear it just for you,
% I got your \[Dm]name written here in a rose tattoo.
% In a \[Am]rose tattoo, in a \[C]rose tattoo
% I got your \[Dm]name written here in a \[Am]rose tattoo.
In a \[Am]rose tattoo, in a \[C]rose tattoo
with \[Dm]pride I'll wear it to the \[Am]grave for you 
In a \[Am]rose tattoo, in a \[C]rose tattoo
I got your \[Dm]name written here in a \[Am]rose tattoo.
In a \[Am]rose tattoo, in a \[C]rose tattoo
Signed and \[Dm]sealed in blood ''I would \[Am]die for you.''
\endchorus

\endsong