\beginsong{Save Tonight}[
    wuw={Eagle-Eye Cherry}, 
    alb={Desireless}, 
    jahr={1997}, 
    pfiii={158}, 
    kssiv={290}, 
    index={Come and close the curtains},
]

\beginverse
Come and \[Am]clos\[F]e the \[C]curtains,\[G] 'cause all we \[Am]need\[F] is \[C]candle\[G]light.
You and me\[Am]\[F] and the b\[C]ottle of \[G]wine and I hold \[Am]you tonight.\[F] \[C] \[G]
Well, we \[Am]know\[F] I'm \[C]going a\[G]way and how I \[Am]wish\[F], I wish it \[C]weren't \[G]so,
So take this\[Am] wine\[F] and d\[C]rink with m\[G]e, \[Am]let's delay our \[F]misery. \[C] \[G]
\endverse

\beginchorus
\lrep Save to\[Am]night\[F], and \[C]fight the break of \[G]dawn.
Co\[Am]me tomorrow\[F], to\[C]morrow I'll be \[G]gone. \rrep 
\endchorus

\beginverse
There's a ^log^ on the ^fire^ and it ^burns^ like ^me for ^you.
Tomorrow^ comes^ with ^one des^ire, ^to take ^me away. ^ ^
It ain't ^easy^ to ^say good^bye, darling ^please^ don't ^start to ^cry,
'cause girl you ^know^ I've ^got to ^go and ^Lord I wish it ^wasn't so. ^ ^
\endverse

\beginchorus
\lrep Save to\[Am]night\[F], and \[C]fight the break of \[G]dawn.
Co\[Am]me tomorrow\[F], to\[C]morrow I'll be \[G]gone. \rrep 

{\nolyrics Solo: \lrep \[Am]\[F]\[C]\[G] \rrep~\rep{4}}
\endchorus

\beginverse
To^morrow co^mes to ^take me a^way. ^I wish that ^I, that ^I could ^stay,
but ^girl you know I've ^got to go^ ^, oh. And ^Lord I wish it ^wasn't so.^ ^
\endverse

\beginchorus 
\lrep Save to\[Am]night\[F], and \[C]fight the break of \[G]dawn.
Co\[Am]me tomorrow\[F], to\[C]morrow I'll be \[G]gone. \rrep~\rep{4}
\lrep \[Am] \[F] To\[C]morrow I'll be \[G]gone. \rrep~\rep{4}
{\nolyrics Solo: \lrep \[Am]\[F]\[C]\[G] \rrep~\rep{4}}
\lrep Save to\[Am]night. \[F] \[C] \[G] \rrep~\rep{4}
\endchorus

\endsong
