\beginsong{Self Esteem}[wuw={The Offspring}, alb={Smash}, jahr={1994}, index={I wrote her off for the tenth time}]

\beginverse*
{\nolyrics Intro: \[Am] \[F] \[C] \[G] \rep{2} \[F] \[G]}
\endverse


\beginverse\memorize
\[Am] I wrote her \[F]off for the \[C]tenth time to\[G]day, \[Am]practiced \[F]all the \[C]things I would \[G]say.
\[Am]When she came \[F]over \[C]I lost my \[G]nerve,\[Am] I took her \[F]back and \[C]made her des\[G]sert.
\[Am]I k\[F]now \[C]I'm being \[G]used, \[Am]that's o\[F]kay man cause I \[C]like the a\[G]buse. \[Am]
I \[F]know she's \[C]playing with \[G]me,\[Am] that's o\[F]kay 'cause I've got \[C]no self es\[G]teem.
\endverse

\beginchorus
Oh \[Am]wey-yeah\[F], ye\[C]ah, \[G]yeah, \[Am]yeah. Oh\[F] ye\[C]ah, yeah\[G], yeah.
\[Am]Oh\[F] \[C]yeah, \[G]yeah, ye\[Am]ah. Oh\[F] \[C]yeah, \[G]yeah, yeah.
\endchorus

\beginverse
^ We make pla^ns to ^go out at ^night, ^I wait till ^two then I ^turn out the ^light.
^This re^jection ^got me so ^low, ^If she keeps it ^up I just ^might tell her ^so.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus
\beginverse*
{\nolyrics \[Bridge]}
\[Dm]When she's \[B&]saying, \[F]oh that she \[C]wants only \[Dm]me, 
then I \[B&]wonder why she \[F]sleeps with my \[C]friends. \[Dm]
When she's \[B&]saying, \[F]oh that I'm \[C]like a di\[Dm]sease,
then I \[B&]wonder how much \[F]more I can \[C]spend. \[Dm]\newpage
Well I \[B&]guess \[F]I should stick \[C]up for my\[Dm]self, 
but I \[B&]really think it's \[F]better this \[C]way. \[Dm]
The more you \[B&]suffer,\[F] the more it \[C]shows you really \[F]care, right? Ye\[G]ah!
\endverse

\beginverse
^Now I'll re^late, ^this little ^bit, ^that happens ^more than I'd ^like to ad^mit.
^Late at ^night, she ^knocks on my ^door, ^she's drunk a^gain and ^looking to ^score.
^I ^know, ^I should say ^no, but^ that's kind of ^hard when she's ^ready to ^go.
^I may be ^dumb, but ^I'm not a ^dweeb, ^I'm just a ^sucker with ^no self es^teem.
\endverse

\beginchorus
\endchorus

\beginverse*
{\nolyrics \[Bridge (wdh.)]}
\endverse

\endsong
