\beginsong{She Loves You}[
    wuw={The Beatles}, 
    alb={Twist and Shout}, 
    jahr={1964},
]

\beginchorus
She \[Em]loves you, yeah, yeah, yeah.
She \[A]loves you, yeah, yeah, yeah.
She \[C]loves you, yeah, yeah, yeah, \[G]yeah!
\endchorus

\beginverse
You \[G]think you've lost your \[Em]love. When I \[Hm]saw her yester\[D]day 
it's \[G]you she's thinking \[Em]of and she \[Hm]told me what to \[D]say,
she said she \[G]loves you and you know that can't be \[Em]bad,
yes she \[Cm]loves you and you know you should be \[D]glad!
\endverse

\beginverse
She ^said you hurt her ^so she ^almost lost her ^mind, 
but ^now she said she ^knows you're ^not the hurting ^kind.
She said she ^loves you and you know that can't be ^bad,
yes she ^loves you and you know you should be ^glad.
\endverse

\beginchorus
She \[Em]loves you, yeah, yeah, yeah.
She \[A]loves you, yeah, yeah, yeah.
With a \[Cm]love like that, you \[D7]know you should be \[G]glad!
\endchorus

\beginverse
You ^know it's up to ^you I ^think it's only ^fair,
if ^I should hurt you ^too a^pologize to ^her. 
Because she ^loves you and you know that can't be ^bad ,
yes she ^loves you and you know you should be ^glad, uuuhh!
\endverse

\beginchorus
She \[Em]loves you, yeah, yeah, yeah.
She \[A]loves you, yeah, yeah, yeah.
With a \[Cm]love like that, you \[D7]know you should be \[G]glad! \[Em] \rep{2}
With a \[Cm]love like that, you \[D7]know you should be \[G]glad!
Yeah, Yeah, Yeah! \[Em]Yeah, Yeah, Yeah, \[C]Yeah, Yeah, Yeah, Ye\[G]ah!
\endchorus


\endsong
