\beginsong{Sloop John B}[
    wuw={The Beach Boys},
    alb={Sloop John B},
    jahr={1966},
    siru={255}, 
    gruen={241}, 
    index={We come on the Sloop John B},
]

\beginverse
We \[G]come on the Sloop \[C]John \[G]B, my grandfather \[C]and \[G]me
Around Nass\[C]au \[G]town we did \[D]roam.
Drinking all \[G]night,\[G7] got into a \[C]fight \[Am]
well I \[G]feel so broke up,\[D] I want to go \[G]home.
\endverse

\beginchorus
So \[G]hoist up the John \[C]B's \[G]sail,
see how the main \[C]sail \[G]sets, 
call for the captain \[C]a\[G]shore,
let me go \[D]home, 
let me go \[G]home, \[G7]
I want to go \[C]home, yeah \[Am]yeah.
Well I \[G]feel so broke up,\[D] I want to go \[G]home.
\endchorus

\beginverse
The ^first mate, he ^got ^drunk and broke in the cap^tain's ^trunk,
the constable had ^to ^come and take him a^way,
sheriff John ^Stone,^ why don't you leave me a^lone, yeah ^yeah.
Well I ^feel so broke up,^ I want to go ^home.
\endverse

\beginchorus
So \[G]hoist up the John \[C]B's \[G]sail, \echo{hoist up the John \[C]B's \[G]sail}
see how the main \[C]sail \[G]sets, \echo{see how the main \[C]sail \[G]sets}
call for the captain \[C]a\[G]shore,
Let me go \[D]home, \echo{Let me go home.}
I want to go \[N.C.]home, \echo{Let me go home.}
Why don't you let me go home?
\echo{Hoist up the John B's sail} Hoist up the John B's...
Well, I \[G]feel so broke up,\[D] I want to go \[G]home. \echo{Let me go home.}
\endchorus

\beginverse
The ^poor cook he caught ^the ^fits and threw away all ^my ^grits
And then he took ^and he ^ate up all of my ^corn.
Let me go ^home, why don't they let me go ^home? ^
This ^is the worst trip^ I've ever been ^on.
\endverse

\beginchorus
So \[G]hoist up the John \[C]B's \[G]sail,
see how the main \[C]sail \[G]sets, call for the captain \[C]a\[G]shore,
let me go \[D]home, \echo{Let me go home.}
I want to go \[G]home, \echo{Let me go \[G7]home.}
why don't they let me go \[C]home? Yeah, \[Am]yeah.
Well I \[G]feel so broke up,\[D] I want to go \[G]home.
\endchorus


\endsong
