\beginsong{Smugglers}[txt={Traditional, 4. Strophe Ian McCalman}, mel={Ian McCalman}]

\beginverse\memorize
The boat \[C] rides south of \[G]Ailsa \[C]Craig in the \[F]waning \[C]of the \[G]light. 
There's \[F]thirty \[G]men in \[C]Lendal \[Am]fit to \[F]make our burden \[G]light. 
And there's \[C]thirty horse in \[G]Hazle\[C]holm with the \[F]halters \[C]on their \[G]heads. 
All \[F]set this \[G]night up \[C]on your \[Am]life if \[Dm]wind and water \[C]speed.
\endverse

\beginchorus
\[Am]Smugglers drink of the \[Em]frenchmens wine 
and the \[Am]darkest night is the \[C]smugglers \[G]time. 
\[F]Away we ran from the \[C]excise\[Am]man. 
It's a \[C]smugglers life for \[F]me. It's a \[C]smugglers \[G7]life for \[C]me.
\endchorus

\beginverse
''Oh ^lass you have a ^cozy ^bed, and ^cattle ^you have ^ten. 
Can ^you not ^live a ^lawful ^life and ^live with lawful ^men?'' 
But ^must I use old ^homely ^goods while there's ^foreign ^gear so ^fine?  
Must ^I drink ^at the ^water^side and ^France so full of ^wine.
\endverse

% \printchorus

\beginverse
Though ^well I like to ^see you ^Kate, with a ^baby ^on your ^knee. 
My ^heart is ^now with the ^gallant ^crew that ^plough through the angry ^sea. 
The ^bitter gale, the ^tightest ^sail, and the ^sheltered ^bay or ^goal. 
It's the ^wayward ^life, it's the ^smugglers ^strife, it's the ^joy of the smugglers ^soul.
\endverse

% \printchorus

\beginverse
And ^when at last the ^dawn comes ^up and the ^cargo’s ^safely ^stored,
like ^sinless ^saints to ^church we'll ^go, God's ^mercy to af^ford.
And it's ^champagne fine for ^communion ^wine and the ^parson ^drinks it, ^too.
With a ^sly wink ^prays ''For^give these ^men, for they ^know not what they ^do.''
\endverse

% \printchorus

\endsong
