\beginsong{Snow (Hey Oh)}[
    wuw={Red Hot Chili Peppers}, 
    alb={Stadium Arcadium}, 
    jahr={2006}, 
    tonart={H},
]
% Transposition Akkorde: -4 

\interlude{Intro: \[Em C G D]}

\beginverse\memorize
\[Em]Come to decide, that the \[C]things that I tried were \[G]in my life, just \[D]to get high on.
\[Em]When I sit alone, \[C]come get a little known, \[G]but I need more than my\[D]self this time.
\[Em]Step from the road to the \[C]sea to the sky and I \[G]do believe what \[D]we rely on.
\[Em] When I lay it on, \[C]come, get to play it on, \[G]all my life to \[D]sacrifice.
\endverse

\beginchorus
\[Em]Hey  \[C]oh,  \[G] listen \[D]what I \[Em]say, \[C]oh,  \[G]  \[D]
I got your, \[Em]hey  \[C]oh,  \[G] now listen \[D]what I \[Em]say, \[C]oh.  \[G]  \[D]
\endchorus

\beginverse
^When will I know that I ^really can't go to the ^well once more time ^to decide on?
^When it's killing me, ^when will I really see ^all that I need to ^look inside.
^Come to believe, that I ^better not leave, be^fore I get my ^chance to ride.
^When it's killing me, ^what do I really need? ^All that I need to ^look inside.
\endverse


\renewcommand{\everychorus}{\textnote{\bf Refrain und Bridge}}
\beginchorus
\[Em]Hey  \[C]oh,  \[G] listen \[D]what I \[Em]say, \[C]oh. \[G] \[D]
Come back and \[Em]hey  \[C]oh,  \[G] look at \[D]what I \[Em]say, \[C]oh. \[G] \[D]
~
The \[C]more I see, the less I know,
the \[Am]more I like to let it go, \[Em]hey oh, oh oh \[C]oh. 
\newpage
\[G]Deep beneath the cover of an\[D]other perfect wonder, where it’s \[Am]so white as snow.
\[G]Privately divided by a \[D]world so undecided, and there's \[Am]nowhere to go.
\[G]Deep beneath the cover of an\[D]other perfect wonder, where it’s \[Am]so white as snow.
\[G]Running through the field where all my \[D]tracks will be concealed and there's \[Am]nowhere to go.
\endchorus

\beginverse
^When to descend, to a^mend for a friend, all the ^channels that have ^broken down.
^ Now you bring it up, ^I'm gonna ring it up, ^just to hear you ^sing it out.
^Step from the road to the ^sea to the sky and I ^do believe what ^we rely on.
^ When I lay it on, ^come, get to play it on, ^all my life to ^sacrifice.
\endverse


\renewcommand{\everychorus}{\textnote{\bf Refrain und Bridge (wdh.)}}
\beginchorus
\endchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
I said, \[G]hey, hey \[D]yeah, oh \[Am]yeah, tell my love now! 
\[G]Hey, hey \[D]yeah, oh \[Am]yeah, tell my love now! 
\[G]Deep beneath the cover of an\[D]other perfect wonder, where it’s \[Am]so white as snow.
\[G]Running through the field where all my \[D]tracks will be concealed, and there's \[Am]nowhere to go.
I said, \[G]hey, hey \[D]yeah, oh \[Am]yeah, tell my love now! 
\[G]Hey, hey \[D]yeah, oh \[Am]yeah.
\endchorus


\endsong
