\beginsong{Streets of London}[wuw={Ralph McTell}, pfii={219}, pfiii={113}, index={Have you seen the old man}]

\beginverse\memorize
\[C]Have you seen the \[G]old man in the \[Am]closed-down \[Em]market, 
\[F]kicking up the \[C]paper, with his \[D7]worn out \[G7]shoes? 
\[C]In his eyes you \[G]see no pride, \[Am]hand held loosely \[Em]at his side,
\[F]yesterday's \[C]paper telling \[G7]yesterday's \[C]news.
\endverse

\beginchorus
So \[F]how can you \[Em]tell me you're \[C]lone\[Am]ly, 
\[D7] and say for you that the sun don't \[G]shine\[G7]? 
\[C]Let me take you \[G]by the hand and \[Am]lead you through the \[Em]streets of London 
\[F]I'll show you \[C]something to \[G7]make you change your \[C]mind.
\endchorus

\beginverse
^Have you seen the ^old girl who ^walks the streets of ^London,
^ dirt in her ^hair and her ^clothes in ^rags? 
^She's no time for ^talking, she ^just keeps right on ^walking,
^ carrying her ^home in ^two carrier ^bags. 
\endverse
 
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse
^In the all night ca^fe at a ^quarter past e^leven, 
^ same old ^man is sitting ^there on his ^own. 
^Looking at the ^world over the ^rim of his ^tea-cup, 
^ each tea lasts an ^hour then he ^wanders home a^lone.
\endverse

\beginchorus
\endchorus

\beginverse
And ^have you seen the ^old man out^side the seaman's ^mission?
^Memory fading ^with the medal ^ribbons that he ^wears. 
^In our winter ^city, the rain ^cries a little ^pity 
for ^one more forgotten ^hero and a ^world that doesn't ^care.
\endverse

\beginchorus
\endchorus

\endsong