\beginsong{Stuck In The Middle With You}[
    wuw={Stealers Wheel},
    alb={Stealers Wheel},
    jahr={1972},
    index={Well I don't know why I came here tonight},
]

\beginverse\memorize
Well I \[D]don't know why I came here tonight.
I've got the \[D]feeling that something ain't right.
I'm so \[G7]scared in case I fall off my chair,
and I'm \[D]wondering how I'll get down the stairs.
\endverse

\beginchorus
\[A]Clowns to the left of me, \[C]Jokers to the \[G]right!
Here I \[D]am stuck in the middle with you.
\endchorus

\beginverse
Yes I'm ^stuck in the middle with you,
and I'm ^wondering what it is I should do.
It's so ^hard to keep this smile from my face.
Losing con^trol and running all over the place.
\endverse

\printchorus

% add interlude hint
\beginchorus
When you \[G7]started off with nothing,
and you're proud that your a self-made man. \[D]
And your \[G7]friends they all come crawling,
slap you on the back and say
\[D]Please ... \[Am7]Please ...
\endchorus

\beginverse
^Trying to make some sense of it all,
but I ^see it makes no sense at all.
Is it ^cool to go to sleep on the floor?
I don't ^think that I can take anymore.
\endverse

\printchorus

% add interlude hint
\beginchorus
When you \[G7]started off with nothing,
and you're proud that your a self-made man. \[D]
And your \[G7]friends they all come crawling,
slap you on the back and say
\[D]Please ... \[Am7]Please ...
\endchorus

\beginverse
Well I ^don't know why I came here tonight,
I've got the ^feeling that something ain't right.
I'm so ^scared in case I fall off my chair,
and I'm ^wondering how I'll get down the stairs.
\endverse

\beginchorus
\[A]Clowns to the left of me, \[C]Jokers to the \[G]right!
Here I \[D]am stuck in the middle with you.
\lrep Yes I'm \[D]stuck in the middle with you... \rrep~\rep{4}
\endchorus

\endsong
