\beginsong{Supergirl}[wuw={Reamonn}, pfiii={143}, index={You can tell by the way}]

\beginverse\memorize
You can tell by the \[F#m]way she walks that she's my \[E]girl.
You can tell by the \[Hm]way she talks she rules the \[D]world.
You can see in her \[F#m]eyes that no one is her \[E]chief.
She's my \[Hm]girl, my super\[D]girl.
\endverse

\beginchorus
And then she'd \[A]say: It's ok, I got \[E]lost on the way 
but I'm a super\[F#m]girl and supergirls don't \[D]cry.
And then she'd \[A]say: It's allright I got \[E]home late last night 
but I'm a super\[F#m]girl and supergirls just \[D]fly.
\endchorus

\beginverse
And then she'd ^say that nothing can go ^wrong.
When you're in ^love what can go ^wrong?
And then she'd ^laugh the night time into the ^day,
pushing her ^fears further a^long.
\endverse
 
\beginchorus
And then she'd \[F#m]say: It's ok, I got \[E]lost on the way 
but I'm a super\[F#m]girl and supergirls don't \[D]cry.
And then she'd \[A]say: It's allright I got \[E]home late last night 
but I'm a super\[F#m]girl and supergirls just \[D]fly.\newpage

Then she'd \[A]shout down the line, tell me she's \[E]got no more time 
cause she's a super\[F#m]girl and supergirls don't \[D]cry.
Then she'd \[A]scream in my face tell me to \[E]leave, leave this place 
cause she's a super\[F#m]girl and supergirls just \[D]fly.
She's a super\[A]girl, a super\[E]girl. 
She's sewing \[F#m]seeds. She's burning trees. 
She's sewing \[D]seeds. She's burning trees. 
She's a super\[A]girl, a super\[E]girl. 
A super\[F#m]girl, my super\[D]girl.
{\nolyrics Ende auf \[A]}
\endchorus

\endsong
