\beginsong{The Family Way}[wuw={The Men They Couldn’t Hang}, alb={The Domino Club}, jahr={1990}, index={Been in jail for twenty years}, kssiv={176}]

\beginverse\memorize
\[Am]Been in jail for twenty years, was \[G]twenty years ago,
\[F]fought a man with my bare hands, \[Am]killed him with a blow.
\[Am]Searched the bars and betting shops in \[G]every part of town,
\[F]swore that night he'd wear a suit, of \[Am]pinewood six feet down.
\endverse

\beginchorus
A changing \[F]world keeps moving \[C]fast, my \[G]yesterday's tomorrow's in the \[Am]past.
When it's \[F]one against the \[C]rest, always \[G]puts you to the \[Am]test
But I \[F]swear I'd do it \[C]all again to\[E]day, 'cause it's the family \[Am]way. \[F]\[C]\[E]
\endchorus

\beginverse
In ^hospital my brother lay, just ^looking at his wounds.
They ^caught him down by London Bridge one ^Friday afternoon.
It was the ^strangeness of his accent, the ^bareness of his purse,
be^cause there was just one of him and ^three to do their worst.
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
My \[C]brother died and left behind a \[G]girl bearing a child.
She \[Am]broke down at the funeral to \[E]see his face defiled.
She \[Am]wears the silver ring of a fian\[G]cee.
\[E]Both were taken to our home, \[Am]shown the \[G]family \[Am]way.
\endchorus

\printchorus

\beginverse
When ^I get out a week today, I'll ^take the London train,
'cause ^two men there have bought a share in ^twenty years of pain.
In ^this old world your kith 'n' kin are ^all that's on your side,
^twenty years won't matter when the ^matter's put to right.
\endverse

\repchorus{2}

\endsong
