\beginsong{The Past Recedes}[
    wuw={John Frusciante}, 
    alb={Curtains}, 
    jahr={2004}, 
]

\begin{minipage}{.85\textwidth}%
\beginverse*
\nolyrics One, two, three, four.
\lrep \[G] \[D] \[Am] \[Em] \rrep \rep{3} 
\[G] \[D] \[Am]
\endverse

\beginverse\memorize
\[G] And then \[D]the past re\[Am]cedes, \[Em]
\[G] and I \[D]won't be in\[Am]volved. \[Em]
\[G] The eff\[D]ort to be \[Am]free  \[Em]
\[G] seems point\[D]less from a\[Am]bove.
\endverse
\end{minipage}%
\begin{minipage}{.15\textwidth}
	\vspace{0pt}
    \begin{flushright}
    \hfill\gtab{D#dim7}{XX(1212)}
    \hfill\gtab{G/h}{X20003}
    \end{flushright}
\end{minipage}%

\beginverse
^ You're looking ^down at ^me, ^
^ I'd rather^ stay be^low, ^
than ^have you sta^ring up at ^me, ^
^'re's no where I ^want to ^go... \[H7]Ohhhhhh!
\endverse

\beginchorus
\[C]Ay, this \[D#dim7]business of how \[Em]long we try to \[D]stay alive.
\[C]Why to \[D#dim7]be here you've first \[Em]got to die, so I \[D]gave it a try.
And \[C]what do you \[G/h]know time was so \[Am]long ago. \[H7]
\endchorus

\beginverse
^ And thinks ^come back you ^see ^
^ to where ^they don't be^long. ^
^ And every ^drop of ^sea ^
^ is the ^whole o^cean. \[H7]
\endverse

\beginchorus
I \[C]lied to the \[D#dim7]greatest thieves about \[Em]anything and \[D]everything.
\[C]I'm a \[D#dim7]figure of for\[Em]gotten speech, I'm \[D]out of reach,
oh, \[C]I can't play it \[G/h]safe, 
but I might \[Am]just in case. \[H7]
\endchorus

% Solo
\beginverse*
\nolyrics
Solo: 
\lrep ^ ^ ^ ^ \rrep \rep{3}
\[G] \[D] \[Am] \[H7]Oh...
\endverse

\beginchorus
\[C] I'm \[D#dim7]disguised as a \[Em]reaching hand, I'm a \[D]working man.
I \[C]don't under\[D#dim7]stand why clockout \[Em]comes so slow \[D]every time.
That's \[C]one line I'd \[G/h]stay right be\[Am]hind.
That's \[C]one line I'd \[G/h]stay right be\[Am]hind. \[H7]
\nolyrics\lrep \[G] \[D] \[Am] \[Em]\rrep \rep{3}
\[G] \[D] \[Am] \[H7]
\[G]
\endchorus

\endsong
