\beginsong{The Water}[
    wuw={Johnny Flynn},
    jahr={2010}, 
    index={All that I have is a river},
]

\beginverse*
\nolyrics
\[C] \[G] \[C] \[F] - \[C] \[G] \[Am] \[F] 
\endverse

\beginverse\memorize
\[C]All that I \[G]have is a \[F]river, 
the \[Am]river is always my \[E]home.
Lord, \[C]take me a\[F]way for I \[Am]just cannot \[F]stay
or I'll \[C]sink in my \[Dm]skin and my \[F]bones.
\endverse

\beginchorus
The \[C]water sus\[G]tains me with\[C]out even \[F]trying,
the \[C]water can't \[G]drown me, I'm \[Am]done with my \[F]dy\[C]ing.
\endchorus

\beginverse
Please ^help me ^build a small ^boat, 
^one that'll ride on the ^flow.
Where the ^river runs ^deep and the ^larger fish ^creep,
I'm ^glad of what ^keeps me a^float.
\endverse

\printchorus

\beginverse
Now ^deeper the ^water I ^sail 
and ^faster the current I'm ^in.
But each ^night brings the ^stars and the ^song in my ^heart
is a ^tune for the ^journeyman's ^tale.
\endverse

\beginchorus
The \[C]water sus\[G]tains me with\[C]out even \[F]trying,
the \[C]water can't \[G]drown me, I'm \[Am]done with my \[F]dying.
\textnote{\bfseries Bridge}
Now the \[E]land that I knew is a \[Am]dream
and the \[E]line on the distance grows \[Am]faint.
So \[C]wide is my \[Dm]river, the ho\[C]rizon a s\[Dm]liver
the \[C]artist has \[G]run out of \[F]paint.
\endchorus

\beginverse
Where the ^blue of the ^sea meets the ^sky 
and the ^big yellow sun leads me ^home.
I'm ^everywhere ^now, the ^way is a ^vow 
to the ^wind of each ^breath by and ^by.
\endverse

\beginchorus
The \[C]water sus\[G]tains me with\[C]out even \[F]trying,
the \[C]water can't \[G]drown me, I'm \[Am]done with my \[F]dy\[C]ing.

{\nolyrics \[C] \[G] \[C] \[F] - \[C] \[G] \[Am] \[F] - \[C] \[C]}
\endchorus

\endsong
