\beginsong{This Is Where I Came In}[
    wuw={Bee Gees}, 
    jahr={2001},
    alb={This Is Where I Came In}, 
    index={I've seen this story},
]

% Verse Type 1
\beginverse
\[Em]I've seen this \[A]story, I've \[C]read it over once or \[Em]twice.
\[Em]I said that \[A]you say, a \[C]little bit of bad ad\[Em]vice.
\[Em]I've been in \[A]trouble, \[C]happened to me all my \[Em]life.
\[Em]I've lied and \[A]you lie, and \[C]who would get the sharpest \[Em]knife?
\endverse

% Verse Type 2
\beginverse
You know I shouldn't ^be somebody like ^that, 
I'm not the kind of ^man to throw his ^hat into the ring and
^ Go down without ^following through, the ^day turns into ^night.
^ Go down, ^following through, the ^day turns into ^night.
\endverse

% Bridge 1
\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[Em]Oh-\[A]ohh, \[Em]oh-\[A]ohh, \[Em]oh-\[A]ohh, \[C]this is just where I came in.
\[G]Hope \[Dsus4/f#]rides \[Em]on, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\[G]Time \[Dsus4/f#]has \[Em]gone, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\endchorus

% Chorus
\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[Em] This is the \[C]danger zone,\[G] this is where \[Am]I came in.
\[Em] They know not \[C]what they do,\[G] forgive them \[Am]of their sins.
\echo{They \[Em]know} they cannot \[C]take away,\[G] what you have \[Am]given me.
\[Em]Oh-\[A]ohh, \[Em]oh-\[A]ohh, \[Em]oh-\[A]ohh, \[C]this is just where I came in. \[Em] \[A] \[C] \[Em]
\endchorus

% Verse Type 1
\beginverse
^Fade into ^color, ^color into black and ^white,
^under the ^bedclothes, ^everything will be al^right.
^I know that ^you know, ^nothing ever stays the ^same,
^said so, I ^said so, the ^love will never speak its ^name.
\endverse

% Verse Type 2
\beginverse
Never gonna ^find somebody like ^you, beauty with a ^brain and a body too. ^
I could never make a ^move on a woman that ^leads me on, 
She's got a ^little bit of something for ^everyone.
^ It's a little too ^late and the ^wolf is on the ^run.
\endverse

% Bridge 2
\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[G]Hope \[Dsus4/f#]rides \[Em]on, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\[G]Time \[Dsus4/f#]has \[Em]gone, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\endchorus

% Chorus
\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[Em] I'd always \[C]told myself,\[G] I would reg\[Am]ret this day.
\[Em] That I would \[C]fall apart,\[G] and watch you \[Am]walk away \echo{to cry.}
\[Em] That you would \[C]cry out loud,\[G] and I would \[Am]stand aside.
\lrep \[Em]Oh-\[A]ohh, \[Em]oh-\[A]ohh, \[Em]oh-\[A]ohh, \[C]this is just where I came in. \rrep
\endchorus

% Bridge 2
\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[G]I \[Dsus4/f#]can \[Em]fly, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\[G]Time \[Dsus4/f#]goes \[Em]by, but I'll go \[Am]anywhere, yes, I'll go \[Am7]anywhere with you.
\endchorus

% Chorus
\renewcommand{\everychorus}{\textnote{\bf Chorus}}
\beginchorus
\[Em] This is the \[C]danger zone,\[G] this is where \[Am]I came in.
\[Em] They know not \[C]what they do,\[G] forgive them \[Am]of their sins.
\echo{They \[Em]know} they cannot \[C]take away,\[G] what you have \[Am]given me.
\lrep \[Em]Oh-\[A]ohh, \[Em]oh-\[A]ohh, \[Em]oh-\[A]ohh, \[C]this is just where I came in. \rrep \rep{3}
\endchorus

\endsong