\beginsong{Torn}[wuw={Nathalie Imruglia}, pfiii={188} index={I thought I saw a man brought to life}]

\beginverse*
{\nolyrics Intro: \[F] \[Fsus4] \[F] \[Fsus4]}
\endverse

\beginverse\memorize
\[F] I thought I saw a man brought to life, \[Am]
he was warm, he came around and he was \[H&]dignified.
He showed me what it was to cry. \[F]
Well you couldn't be that man I adore, \[Am]
you don't seem to know, seem to care what your \[H&]heart is for,
but I don't know him anymore.
\endverse

\beginverse*
Bridge:
There's \[Dm]nothing where you used to lie, \[C]the conversation has run dry,
\[Am] that's what's going on...\[C] Nothing's fine, I'm \[F]torn!
\endverse

\beginchorus
I'm all out of \[C]faith, this is how I \[Dm]feel.
I'm cold and I am \[H&]shamed lying naked on the \[F]floor,
illusion never \[C]changed into something \[Dm]real.
I'm wide awake and \[H&]I can see the perfect sky is \[F]torn,
you're a little late,\[C] I'm already \[Dm]torn. \echo{\[H&]torn.}
\endchorus

\beginverse
^ So I guess the fortune teller's right. ^
I should have seen just what was there and not some ^holy light
to crawl beneath my veins and now: 
\endverse

\beginverse*
Bridge:
\[Dm] I don't care I have no luck,\[C] I don't miss it all that much, \[Am]
there's just so many \[C]things... That I can't touch, I'm \[F]torn!
\endverse

\beginchorus
\endchorus

\beginverse*
Bridge:
There's \[Dm]nothing where you used to lie,\[C] my inspiration has run dry, \[Am]
that's what's going \[C]on... Nothing's right, I'm \[F]torn!
\endverse

\beginchorus
\endchorus

\endsong
