\beginsong{Toxic}[
    wuw={Britney Spears}, 
    alb={In the Zone},
    jahr={2004},
    index={Baby, can't you see},
]

\beginverse
\[Am] Baby, can't you see,\[Am] I'm calling.
\[Am] A guy like you\[Am] should wear a warning.
\[C] It's dangerous,\[E7] I'm fal\[Am]ling.
\endverse

\beginverse
^ There's no escape,^ I can't wait.
^ I need a hit,^ Baby, give me it.
^ You're dangerous,^ I'm loving ^it.
\endverse

\beginverse*
^ Too high,^ can't come down,
^ losin' my head, spinnin' ^'round and 'round. ^
^ Do you feel me ^now? \[Am]
\endverse

\beginchorus
Oh, the \[Am]taste of your lips, I'm \[C]on a ride.
\[H7]You're toxic, \[B&7]I'm slippin' under
with a \[Am]taste of a poison \[C]paradise.
I'm ad\[F7]dicted to you, don't you \[E7]know that you're toxic? \[Am] \[C]
And I \[F7]love what you do, don't you \[E7]know that you're toxic? \[Am] \[C] \[F7] \[E7]
\endchorus

\beginverse
^ It's getting late^ to give you up.
^ I took a sip^ from my devil's cup.
^ Slowly,^ it's taking over me. ^
\endverse

\beginverse*
^ Too high,^ can't come down,
^ it's in the air and it's ^all around.
^ ^ Can you feel me now? ^ \[Am]
\endverse

\printchorus

\beginverse*
\[Am] \[C] \[H7] \[B&7]
\[Am] \[C] \[F7] \[E7]
\endverse

\beginchorus
\lrep Oh, the \[(Am)]taste of your lips, I'm \[(C)]on a ride.
\[H7]You're toxic, \[B&7]I'm slippin' under
with a \[Am]taste of a poison \[C]paradise.
I'm a\[F7]ddicted to you, don't you \[E7]know that you're toxic? \rrep 

\[Am] Intoxicate me now,\[C] with your lovin' now
\[H7] I think I'm ready now \echo{\[B&7]I think I'm ready now}
\[Am] Intoxicate me now,\[C] with your lovin' now,
\[F7 ]I think I'm ready now. \[(E7)]
\endchorus

\endsong
