\beginsong{Tribute}[wuw={Tenacious D}, alb={Tenacious D}, jahr={2001}, pfiii={162}, kssiv={276}, index={This is the greatest and best song}]

\beginverse*
{\nolyrics Intro: \[Am]}
This is the greatest and best song in the world... Tribute.
\endverse

\beginverse
\[Am]Long time ago me and my brother Kyle here, we was hitchhikin' down a long and lonesome road. 
All of a sudden, there shined a shiny demon... In the middle of the road. 
And he said: '\[A5 Muted]Play the best song in the world, or I'll eat your souls.'
\[Am]Well me and Kyle, we looked at each other, and we each said: 'Okay.'
\endverse

\beginchorus 
And we \[Am]played the first thing that \[G]came to our heads, \[F]just so happened to be.
The \[Am]best song in the \[G]world, it was the \[F]best song in the world.
\[D]Look into my eyes and it's \[F]easy to see: 
One and \[C]one make two, two and \[G]one make three, It was \[F]destiny. 
\[D]Once every hundred-thousand \[F]years or so, 
when the \[C]sun doth shine and the \[G]moon doth glow 
and the \[F]grass doth grow...
\endchorus

\beginverse
\[Am]Needless to say, the beast was stunned. 
Whip-crack went his schwumpy tail, and the beast was done. 
He asked us: \echo{Schnief.}'Be you angels?'
And we said 'Nay. We are but men.', Rock! 
\[D]Ahhh, \[F]ahhh, \[C]ahhh-ah-\[G]ah, \[F]ohhh, wh\[F]oah, ah-whoah-\[Am]oh!
\endverse

\beginchorus
This is not the \[G]greatest song in the \[Am]world, no. This is just a \[G]tribute. \[Am]
\[Am]Couldn't remember the \[G]greatest song in the \[Am]world, nooo. No!
This is a \[G]tribu\[Am]te, oh,\[G] to the greatest \[D]song in the \[F]world, 
All \[Am]right!\[G] It was the greatest \[D]song in the \[F]world, 
All \[Am]right! It-a was the \[G]best muthafuckin' song the \[D]greatest song in the \[F]world. 
\endchorus

\beginverse*
a cappella
\[Am] \[G] \[D/f#] \[F] \[Am] \[G] \[D/f#] \[F]
\[Am]And the peculiar \[G]thing is this my friends: the \[D/f#]song we sang on that \[F]fateful night it \[Am]didn't actually sound \[G]anything like \[D/f#]this song. \[F]
\endverse

\beginchorus
This is just a \[Am]tribute! You \[G]gotta be\[D/f#]lieve me! 
And I \[F]wish you were \[Am]there! Just a \[G]matter of o\[D/f#]pinion. 
\[F]Ah, fuck! \[Am]Good God, \[G]God lovin', 
\[D/f#]So surprised to \[F]find you can't stop it. \[Am]
On fire, \[G]really on fire. \[D/f#]\[F]\echo{Laut-Gesagt}
\[E] \[F] \[G]All ri\[E]ght! \[F] \[G]All ri\[E]ght! \[F] \[F]
{\nolyrics Ende: \[Am]}
\endchorus

\endsong
