\beginsong{Warriors Of The World United}[wuw={Manowar}, jahr=2002, alb={Warriors of the World}]


\renewcommand{\everychorus}{\textnote{\bf Intro}}
\beginchorus\nolyrics
Drums only:~~ \[-- --]
with Bass:~~ \[Em ~~~ Em] 
Guitar Part 1:~~ \[Em ~~~ Em ~~~ Em ~~~ C ~~~~~ C ~~~~~ Em ~~~ Em]
Guitar Part 2:~~ \[Em ~~~ Em ~~~ Em ~~~ C ~~ G--Em ~~ Em]
Guitar Part 3:~~ \[Em ~~~ Em ~~~~ C ~~~~~ C ~~ G--Em ~~~ Em]

Choir:~~\lrep \[G--Em]{~~~~~Ho}-ho-ho-\[G--D]{~~~~~ho}-hooo, \[C]ho-\[G--]ho-\[F#--]ho-\[Em]hooo \rrep \[Em ~~~ Em]
\endchorus

\beginverse
\[Em]Here our soldiers stand from all around the world,
\[C]waiting in a line to hear the battle cry.
\[Em]All are gathered here, victory is near,
the \[C]sound will fill the hall, bringing power to us all.
\[C--D--] \[Em]We alone are fighting for metal that is true,
we \[C]own the right to live the fight, we're here for all of you.
Now \[Em]swear the blood upon your steel will never dry,
\[C]stand and fight together, beneath the metal sky.
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\[G--Em]{~~~~~Brothers} everywhere, \[G--]raise your \[D]hands into the air.
We're \[C]warriors, \[G]warriors \[F#]of the \[Em]world.
\[G--Em]{~~~~~Like} thunder from the sky, \[G--D]{~~~~~sworn} to fight and die.
We're \[C]warriors, \[G]warriors \[F#]of the \[Em]world.
\endchorus

\beginverse
\[Em]Many stand against us but they will never win,
we \[C]said we would return and here we are again.
To \[Em]bring them all destruction suffering and pain,
we are the \[C]hammer of the gods we are thunder wind and rain.
\[C--D--] \[Em]There they wait in fear with swords in feeble hands,
with \[C]dreams to be a king first one should be a man.
I \[Em]call them out and charge them all with a life that is a lie,
and \[C]in their final hour they shall confess before they die.
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
\[Hm] If I should \[F#]fall in battle,\[Hm] my brothers who \[F#]fight by my side
\[Em] Gather my \[F#]horse and weapons \[Hm]tell my family \[F#]how I died
\[C]Until then \[G]I will be strong, \[Dm]I will fight for \[Am]all that is real 
\[Dm]All who \[Am]stand in my way will \[D]die by steel!
\endchorus


\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\lrep \[G--Em]{~~~~~Brothers} everywhere, \[G--]raise your \[D]hands into the air.
We're \[C]warriors, \[G]warriors \[F#]of the \[Em]world.
\[G--Em]{~~~~~Brothers} everywhere, \[G--]raise your \[D]hands into the air.
We're \[C]warriors, \[G]warriors \[F#]of the \[Em]world.
\[G--Em]{~~~~~Like} thunder from the sky, \[G--D]{~~~~~sworn} to fight and die.
We're \[C]warriors, \[G]warriors \[F#]of the \[Em]world. \rrep
\endchorus

\endsong