\beginsong{We are the World}[wuw={USA for Africa}, jahr=1985]

\transpose{+3}

\beginverse\memorize
\[E]There comes a time, when we \[A]heed a \[H]certain \[E]call.
When the \[A]world must \[H]come together as \[E]one.
There are \[C#m]peole dying, and it's \[G#m]time to lend a hand,
to \[F#m]life the \[A]greatest gift of \[Hsus4]all. \[H]
\endverse

\beginverse
^We can't go on pre^tending day by ^day,
that some^one, some^where will soon make a ^change.
We are ^all a part of God's ^great big family
and the ^truth, you ^know, Love is all we ^need. ^ ^
\endverse

\beginchorus
We are the \[A]world\[H] we are the \[E]children.
We are the \[A]ones who make a brighter \[H]day so lets start \[E]giving.
There's a \[C#m]choice we're making, we're \[G#m]saving our own lives.
It's \[F#m]true we'll make a better \[H]day, just you and \[E]me.
\endchorus

\beginverse
^Send them your heart so they'll ^know that someone ^cares
and their ^lives will ^be stronger and ^free.
As ^God has shown us by ^turning stones to bread,
so we ^all must lend a helping ^hand. ^
\endverse

\printchorus

\renewcommand{\everychorus}{\textnote{\bf Bridge}}
\beginchorus
When you're \[C]down and out, there \[D]seems no hope at \[E]all,
but if your \[C]just believe there's \[D]no way we can \[E]fall.
Let us \[C#m]realize that a \[G#m]change can only come,
when \[F#m]we stand together as \[H]one.
\endchorus

\printchorus


\renewcommand{\everychorus}{\textnote{\bf Refrain (Transp.)}}
\transpose{2}
\beginchorus
We are the \[A]world\[H] we are the \[E]children.
We are the \[A]ones who make a brighter \[H]day so lets start \[E]giving.
There's a \[C#m]choice we're making, we're \[G#m]saving our own lives.
\lrep It's \[F#m]true we'll make a better \[H]day, just you and \[E]me. \rrep
\endchorus

\endsong