\beginsong{What's up?}[
    wuw={Four Nonblondes}, 
    pfii={260}, 
    pfiii={135}, 
    kssiv={271}, 
    index={Twenty-Five years of my live},
]

\beginverse*
{\nolyrics Intro: \[A] \[Hm] \[D] \[A]}
\endverse 

\beginverse\memorize
\[A]25 years of my life and still, 
\[Hm]I'm trying to get up that great big hill of \[D]hope, for a desti\[A]nation.
I \[A]realized quickly when I knew I should, 
that the \[Hm]world was made up of this brotherhood of \[D]men, for whatever that \[A]means.
\endverse

\beginverse*
And so I ^cry sometimes when I lie in bed, 
just to ^get it all out what’s in my head and I^, I’m feeling a little pe^culiar.
And so I a^wake in the morning and I step outside, 
and I ^take a deep breath and I get real high and I,^ scream from the top of my lungs, 
What’s going ^on?
\endverse

\beginchorus
\lrep And I said: \[A]Hey-hey-hey-he-y, \[Hm]Hey-hey-hey
I said: \[D]Hey, what's going \[A]on? \rrep \rep{2}
\endchorus

\beginverse
And I ^try, oh my God do I ^try, 
I try all the ^time, in this insti^tution.
And I ^pray, oh my God do I ^pray, 
I pray every single ^day, for revo^lution.
\endverse

\beginverse*
And so I ^cry sometimes when I lie in bed, 
just to ^get it all out what’s in my head and I^, I’m feeling a little pe^culiar.
and so I ^wake in the morning and I Step outside, 
and I ^take a deep breath and I get real high and I^, scream from the top of my lungs, 
What’s going ^on?
\endverse

\beginchorus
\lrep And I said: \[A]Hey-hey-hey-he-y, \[Hm]Hey-hey-hey
I said: \[D]Hey, what's going \[A]on? \rrep \rep{4}
\endchorus

\beginverse
^25 years and my life is still, 
^trying to get up that great big hill of ^hope, for a desti^nation.
\endverse

\endsong
