\beginsong{When I'm Sixty-Four}[
    wuw={The Beatles},  
    alb={Sgt. Peppers Lonely Hearts Club Band}, 
    jahr={1967}, 
]

\beginverse*
\nolyrics Intro: \[C] \[F] \[G] \[C-G-C]
\endverse

\beginverse\memorize
\[C]When I get older losing my hair, many years from \[G]now,
will you still be sending me a Valentine, \[G]Birth\[a]day \[b&]gree\[h]tings, \[C]bottle of wine?
\[C]If I'd been out till quarter to three, \[C7]would you lock the \[F]door?
\[F]Will you still \[Fm]need me, \[C]will you still \[A]feed me, \[D]when I'm \[G7]sixty-\[C-G-C]four?
\endverse

\beginchorus
\[Am]Ohhh-\[G]ohhh-\[Am]ohhh, \[Am]you'll be older \[E]too,
\[Am]and if you \[D7]say the word, \[F]I could \[G]stay with \[C]you.  \[G] \[g-h-d-f]
\endchorus

\beginverse
^I could be handy, mending a fuse, when your lights have ^gone.
You can knit a sweater by the fireside, ^Sun^day ^mor^nings ^go for a ride.
^Doing the garden, digging the weeds, ^who could ask for ^more?
^Will you still ^need me, ^will you still ^feed me, ^when I'm ^sixty-^four?
\endverse

\beginchorus
\[Am]Every summer we can rent a cottage in the Isle of \[G]Wight, if it's not too \[Am]dear.
\[Am]We shall scrimp and \[E]save, \[Am] Grandchildren \[D7]on your knee,
\[F]Vera, \[G]Chuck and \[C]Dave. \[G] \[g-h-d-f]
\endchorus

\beginverse
^Send me a postcard, drop me a line, stating point of ^view.
Indicate precisely what you mean to say, ^yours ^sin^cere^ly, ^wasting away.
^Give me your answer, fill in a form, ^mine for ever^more.
^Will you still ^need me, ^will you still ^feed me, ^When I'm ^sixty-^four?
\nolyrics Outro: \[C] \[F] \[G] \[C-G-C]
\endverse

\endsong
