\beginsong{Wild World}[wuw={Cat Stevens, 1970}, pfii={210}, pfiii={112}, index={Now, that I‘ve lost everything to you}, gruen={242}, kssiv={228}]

\beginverse
\[Am] Lalalala\[D7]lalala-la-la-la\[G]la, Lalalala\[C]lalala-la-la-la\[F]la, 
Lalalala\[Dm]lalala-la-la-la\[E]la-la.
\[Am]Now that I've \[D7]lost everything to \[G]you, you say you \[C]want to start something \[F]new.
And it's \[Dm]breaking my heart you're \[E]leaving, baby I'm grieving. 
\[Am] But if you want to \[D7]leave take good \[G]care, hope you have a \[C]lot of nice things to \[F]wear,
but then a \[Dm]lot of nice things turn \[E]bad out \[G]there
\endverse

\beginchorus
\[C] Oh, \[G]baby, baby it's a \[F]wild world, \[G]It's hard to get \[F]by just upon a \[C]smile. \[D] \[E]
\[C] Oh, \[G]baby, baby it's a \[F]wild world, I'll \[G]always re\[F]member you like a \[C]child, girl. \[D] \[E]
\endchorus


\beginverse
^ You know I've seen a ^lot of what the world can ^do, and it's ^breaking my heart in ^two,
'cos I ^never want to see you ^sad girl, don't be a bad girl.
^ But if you want to ^leave take good ^care, hope you make a ^lot of nice friends out ^there,
but just re^member there's a lot of bad ^and be\[G]ware.
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
\endchorus

\beginverse
^Lalalala^lalala-la-la-la^la, Lalalala^lalala-la-la-la^la, 
Lalalala^lalala-la-la-la^la-la, baby I love you!
^ But if you want to ^leave take good ^care, hope you make a ^lot of nice friends out ^there,
but just re^member there's a lot of bad ^and be\[G]ware
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain (x2)}}
\beginchorus
\endchorus


\endsong 
