\beginsong{Wind Of Change}[wuw={Scorpions}, pfiii={160}, index={I follow the Moskva}]

\beginverse*
{\nolyrics Intro: \[F] \[Dm] \[F] \[Dm] \[Am7] \[Dm] \[Am7] \[G]}
\endverse

\beginverse\memorize
\[C]I follow the \[Dm]Moskva down to Gorky \[C]Park,
listening to the \[Dm]wind of \[Am7]chan\[G]ge.
\[C]An August summer\[Dm]night soldiers passing \[C]by,
listening to the \[Dm]wind of \[Am7]chan\[G]ge.
\endverse

\beginverse*
{\nolyrics Zwischenspiel: \[F] \[Dm] \[F] \[Dm] \[Am7] \[Dm] \[Am7] \[G]}
\endverse

\beginverse
^The world is closing ^in, did you ever ^think,
that we could be so ^close, like ^bro^thers.
^The future's in the ^air, I can feel it every^where,
blowing with the ^wind of ^chan^ge.
\endverse

\beginchorus
\[C]Take \[G]me to the \[Dm]magic of the \[G]moment
on a \[C]glory \[G]night.
Where the \[Dm]children of tomo\[G]rrow dream a\[Am]way,
in the wind of ch\[G]ange.
\endchorus

\beginverse
^Walking down the ^street, distant memo^ries 
are buried in the ^past fo^re^ver.
^I follow the ^Moskva down to Gorky ^Park,
listening to the ^wind of ^chan^ge.
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\endchorus

\beginverse*
\[Am]The wind of change blows \[G]straight, into the face of \[Am]time,
like a stormwind that will \[G]ring, the freedom bell for peace of  \[C]mind.
Let your balalaika \[Dm]sing, what my guitar wants to \[E]say.
\endverse

\beginverse*
{\nolyrics Solo: \[F] \[G] \[E] \[Am] \[F] \[G] \[E7] \[Am] \[Dm] \[E]}
\endverse
\renewcommand{\everychorus}{\textnote{\bf Refrain}}
\beginchorus
\[C]Take \[G]me to the \[Dm]magic of the \[G]moment
On a \[C]glory \[G]night
Where the \[Dm]children of tomo\[G]rrow share their dr\[Am]eams
with you and m\[G]e
\endchorus

\beginverse*
{\nolyrics Outro: \[F] \[Dm] \[F] \[Dm] \[Am7] \[Dm]}
\endverse

\endsong
