\beginsong{Wonderwall}[wuw={Oasis}, alb={(What’s the Story) Morning Glory?}, jahr={1995}, pfiii={144}, kssiv={278}, siru={227}, index={Today is gonna be the day}]

\beginverse*
{\nolyrics Intro: \[Em7] \[G] \[Dsus4] \[A7sus4] \[Em7] \[G] \[Dsus4] \[A7sus4] \rep{2}}
\endverse

\beginverse\memorize
 \[Em7]Today is \[G]gonna be the day
That they're \[Dsus4]gonna throw it back to \[A7sus4]you,
\[Em7]By now you \[G]should have somehow
Rea\[Dsus4]lised what you gotta \[A7sus4]do.
\[Em7]I don't believe that \[G]anybody \[Dsus4]feels the way I \[A7sus4]do
About you \[Cadd9]now. \[Dsus4] \[A7sus4]
\endverse

\beginverse
^Back beat, the ^word is on the street
That the ^fire in your heart is ^out,
^I'm sure you've ^heard it all before,
But you ^never really had a ^doubt.
^I don't believe that ^anybody ^feels the way I ^do
About you ^now. ^^
\endverse

\beginverse*
And \[Cadd9]all the roads we \[Dsus4]have to walk are \[Em7]winding,
And \[Cadd9]all the lights that \[Dsus4]lead us there are \[Em7]blinding,
\[Cadd9]There are many \[Dsus4]things that I would \[G]like to \[Dsus4/f#]say to \[Em7]you
But I \[G]don't know \[A7sus4]how. \[Dsus4]
\endverse

\beginchorus
Because \[Cadd9]maybe, \[Em7] \[G] you're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G]
And \[Em7]after \[Cadd9]all, \[Em7] \[G] you're my \[Em7]wonder\[Cadd9]wall. \[Em7] \[Dsus4]
\endchorus

\beginverse
^Today was ^gonna be the day,
But they'll ^never throw it back at ^you,
^By now you ^should have somehow
Rea^lised what you've gotta ^do.
^I don't believe that ^anybody ^feels the way I ^do
About you ^now. ^^
\endverse

\beginverse*
And \[Cadd9]all the roads that \[Dsus4]lead you there are \[Em7]winding,
And \[Cadd9]all the lights that \[Dsus4]light the way are \[Em7]blinding,
\[Cadd9]There are many \[Dsus4]things that I would \[G]like to \[Dsus4/f#]say to \[Em7]you
But I \[G]don't know \[A7sus4]how. \[Dsus4]
\endverse

\renewcommand{\everychorus}{\textnote{\bf Refrain (wdh.)}}
\beginchorus
I said \[Cadd9]maybe, \[Em7] \[G] 
You're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G]
You're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G]
You're \[Em7]gonna be the one that \[Cadd9]saves me, \[Em7] \[G] \[Dsus4] \[Em7]
\endchorus

\endsong
