\beginsong{The green fields of France}[wuw={Eric Bogle, 1976}, index={Well, how do you do}]

\markboth{\songtitle}{\songtitle}

\beginverse
Well, \[G]how do you \[Em]do, young \[C]Willie Mc\[Am]Bride?
Do you \[D]mind, if I sit here down be\[G]side your \[C]grave\[G]side
and rest for a \[Em]while 'neath the \[D]warm summer \[Am]sun?
I've been \[D]walking all day, and \[G]I'm \[C]nearly \[G]done.
And I see by your \[Em]gravestone you \[C]were only nine\[Am]teen,
when you \[D]joined the great fallen in \[G]nineteen-\[D]sixteen.
Well, I \[G]hope you died \[Em]quick
and I \[Am]hope you died \[C]clean.
Or \[D]Willie McBride, was is it \[G]slow and \[D]ob\[G]scene?
\endverse

\beginchorus
Did they \[D]beat the drum \[D7]slowly,
did they \[C]play the fife \[G]lowly,
did they \[D]sound the dead \[D7]march, as they \[C]lowered you \[D]down,
did the \[C]band play the last post and \[G]cho\[Em]rus,
did the \[G]pipes play the ''\[C]Flowers of the \[D7]Fo\[G]rest''?
\endchorus

\beginverse
And \[G]did you leave a \[Em]wife or a \[C]sweetheart \[Am]behind?
In \[D]some loyal \[D7]heart is your \[C]memory en\[G]shrined.
And though you \[Em]died back in \[C]nineteen-\[Am]sixteen,
to that \[D]loyal \[D7]heart you're for\[C]ever \[G]19.
Or are you a \[Em]stranger without \[C]even a \[Am]name,
for\[D]ever \[C]enshrined behind \[G]some old glass \[D7]pane,
in \[G]an old photo\[Em]graph torn, \[C]tattered and \[Am]stained
and \[D]faded to \[D7]yellow in a \[C]brown leather \[D]frame?
\endverse

\beginverse
The ^sun's shining ^down on these ^green fields of ^France,
the ^warm wind blows ^gently and the ^red poppies ^dance,
the trenches have ^vanished long ^under the ^plow.
No ^gas, no barbed ^wire, no ^guns firing ^now!
But ^here in this ^graveyard it's ^still ''No Man's ^Land'',
the ^countless white ^crosses in ^mute witness ^stand
to ^man's blind ^indifference to ^his fellow man
and a ^whole gene^ration that were ^butchered and ^damned.
\endverse

\beginverse
And I ^can't help but ^wonder, oh ^Willie Mc^Bride.
Do ^all those, who ^lie here, ^know why they ^died,
did you ^really be^lieve them when they ^told you the cause,
did they ^really be^lieve that this ^war would end ^wars?
Well, the ^suffering, the ^sorrow, the ^glory, the ^shame,
the ^killing and ^dying, it ^was all done in ^vain.
Oh ^Willie Mc^Bride, it all ^happened again
and ^again, ^and again, ^and again, ^and again.
\endverse

\endsong

\beginscripture{}
Das Lied beschreibt die Gedanken über ein junges Opfer des Ersten Weltkriegs in Flandern oder Nordfrankreich. Den Daten entsprechend könnte es sich um den in Authuille begrabenen William McBride handeln. Genauso gut könnte es jedoch auch sein, dass das Lied von einer fiktive Person handelt.
\endscripture

\begin{intersong}

\end{intersong}