%!TEX root = ../Single-Song.tex
\beginsong{Hollywood Hills}[wuw={Sunrise Avenue}, index={Now this is not the time}, alb={Out of Style}, jahr={2011}]

\beginverse
{\nolyrics Intro: \[C]\[G]\[Am]\[G]\[C]}

Now this \[C]is not the time or the place for a broken-hear\[G]ted, 
'cause this is the end of the \[Am]rainbow 
where no one can be too \[Am]sad... \[G]
No I \[C]don't wanna leave, but I must keep moving a\[G]head,
'cause my life belongs to the \[Am]other side 
behind the great ocean's \[Am]waves.
\endverse

\beginchorus
\[C] Bye bye, Hollywood Hills, I'm gonna
\[G] miss you, where ever I go, I'm gonna
\[Am] come back to walk these streets again.
\[F] Bye bye, Hollywood Hills forever.
\endchorus

\beginverse
Thank \[C]you for the morning walks on the sweet sun\[G]set
and for the hot night \[Am]moments,
for the fantasy in my \[Am]bed... \[G]
I take \[C]part of you with me now and you won't get it \[G]back
and a part of me will \[Am]stay here, 
you can keep it forever, \[Am]dear.
Ohhh-\[D]Ohhh... \[F]
\endverse

\beginchorus
\[C] Bye bye, Hollywood Hills, I'm gonna
\[G] miss you, where ever I go, I'm gonna
\[Am] come back to walk these streets again.
\[F] Remember, that we had fun together.

\[C] Bye bye, Rodeo Girls, I'm gonna
\[G] love you, where ever I go, I'm gonna
\[Am] come back so we can play together.
\[G] Bye bye, Hollywood Hills forever.
\endchorus

\beginverse
^ Long distance love doesn't ^work,
all the miles in between getting ^naughty.
No I don't wanna go, I don't wanna go!
\endverse

\beginchorus
\endchorus
\endsong

\beginscripture

\endscripture

\begin{intersong}
\end{intersong}